\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{latexsym}

%\newcommand{\norm}[1]{ \left|  #1 \right| }
%\newcommand{\ifof}{\Leftrightarrow}

%\renewcommand{\Re}{{\mbox{Re}}}
%\def\bs{\begin{split}}

%\def\dir{{\mbox{\rm dir}}}
%\def\dist{{\mbox{\rm dist}}}

%\def\eps{\varepsilon}
\def\vphi{\varphi}
\def\lam{\lambda}
%\def\Om{\Omega}
\def\de{\delta}
%\def\sh{\sinh}
%\def\ch{\cosh}
%\def\th{\tanh}
%\def\F{{\cal F}}
\newcommand{\scr}{\mathscr}
\newcommand{\ud}{\mathrm{d}}

\newtheorem{theorem}[subsection]{Theorem}
\newtheorem{lemma}[subsection]{Lemma}
\newtheorem{corollary}[subsection]{Corollary}

\newtheorem{remarks}[subsection]{Remarks}
\newtheorem{definition}[subsection]{Definition}

%\include{psfig}

\title{$ L^p$ estimates for the iterated Hardy-Littlewood maximal operator}
\author{Shijun Zheng \\
        {\normalsize {\sl Department of Mathematics }} \\
        {\normalsize {\sl University of New Mexico }}\\
        {\normalsize {\sl Albuquerque, NM 87131}}\\
        {\normalsize {\sl USA}}\\
and\\      
{Weiyi Su}\\
    {\normalsize {\sl Department of Mathematics }} \\
        {\normalsize {\sl Nanjing University}}\\
        {\normalsize {\sl Nanjing, 210093 }}\\
        {\normalsize {\sl China, P.R.}}\\   
        }
\date{January 10, 1996}

\begin{document}
\maketitle
%\tableofcontents

%\begin{review}
$\mathbf{Mathematical\; Review}$ ({\em Approx. Theory and Its Applications}, {\bf 14}(3),
1998, 36-54)

Let $f$ be a locally integrable function in the $n$-dimensional Euclidean space $ R^n$ and define the Hardy-Littlewood maximal function as follows:
$Mf(x)=\sup|Q|^{-1}\int_Q|f|$, where the sup is taken over all the balls $Q$ centered at $x$. The $k$th iteration of $M$ is defined by induction:
$M^kf(x)=M(M^{k-1}f)(x)$. The main result of the paper can be formulated as follows: Theorem 2.3: (1) If $1<p<\infty$, then the $L^p$ norms of $f$ and $M^kf$
are equivalent for $k\geq1$. Let $f\in L^1( R^n), {\rm supp}\,f\subset B$, where $B$ is a finite ball; then (2) for $p=1, \int_BM^kf<\infty$ iff
$\int_B|f|(\log|f|)^k<\infty$, and (3) for $0<p<1,\ \int_B(M^kf)^p<\infty$ iff $\int_B|f|(\log|f|)^{k-1}<\infty$. 

The second part of the paper is devoted to the generalizations of these and similar results to the case of linear spaces over local fields.

%\end{review}

\begin{abstract}

In light of two measure estimate inequalities from \cite{L} for the
iterated Hardy-Littlewood maximal operator $M^k f$, certain
equivalence between $ M^k f$ and the Zygmund class $ L\log^a L  $ are
established on $\mathbb{R}^n$, so that we generalize Stein's $ L\log L
$ theorem. In Section 3, a simple induction enables us to prove such
extensions on $K^n$, the n-dimensional linear space over a local field $K$,  
without recoursing to Leckband's result.

\end{abstract}


\section{Introduction}

Using the argument of nonincreasing rearrangement of $f$, Leckband
obtained (for technique reasons, we record as follows):

{\bf Theorem L} Let $\lam >0$ and $k\in \mathbb{N} $. Then there exist
constants $A>1$ and $0<B<1$ dependent only on $n$, $k$ so that
$$ 
(i) \qquad |\{ x\in \mathbb{R}^n: M^k f(x)>\lam  \} | \le
A\int_{\{|f|>\lam /A   \} } \frac{|f(x)|}{\lam } (1+ \log^+\frac{|f(x)|}{\lam }  )^{k-1}dx, 
$$

$$  
(ii) \qquad |\{ x\in \mathbb{R}^n: M^k f(x)>B \lam  \} | \le
A\int_{\{|f|>\lam  \} } \frac{|f(x)|}{\lam } (1+ \log^+\frac{|f(x)|}{B\lam }  )^{k-1}dx, 
$$
where the set $\{ g>\lam \} =\{ x\in \mathbb{R}^n: g(x)>\lam \}$ and
the function $ \log^+ x = \max\{\log x,0 \}, x\ge 0  $.

\vspace{0.2in}

The following pointwise estimate in P\'erez\cite{Perez} may have intimate relation with
Leckband inequality above.

For $k=1,2,\dots$, 
$$  M^{k+1} f(x) \sim  M_{\vphi_k } f(x),$$
where $ \vphi_k(t)= t(1+\log^+t)^k $.


\vspace{.4in}

Let $(X,d, \mu)$ be a space of homogeneous type, where $d$ is a
quasi-metric on the set $X$ and $\mu$ is a doubling Borel measure;
moreover, $\mu(B(x,r))<\infty$, $ B(x,r)=\{y\in X: d(x,y)<r \} $.  

Macias and Segovia showed that there exists a quasi-metric $\rho$,
generating the same topology as $d$. Among other properties,
there is a $\delta_0>0$ such that $\rho (x,y)^{\delta_0} $ is a metric
on $X$. (When $X=\mathbb{R}^n$, $d(x,y)=|x-y|$, we may take $\rho (x,y)=|x-y|^n$,
then $\delta_0 =1/n$.

%\section{ $L^p$ estimates for $M^k f$ on $\mathbb{R}^n$}

Note.
%\section{Appendix C: Kernel formula} 
%\input{appendC.tex}  

\begin{thebibliography}{99}
%\input{ref.tex}
\bibitem{HanHof} 
Y.S. Han and S.Hofmann, $T1$ theorems for Besov and Triebel-Lizorkin spaces,
{\em Tran.Amer.Math.Soc.}, {\bf 337}(1993), no.2, 839-853.

\bibitem{L}
Leckband, M. A. A note on maximal operators and reversible weak type
inequalities, {\em Proc. Amer. Math. Soc.} {\bf 92} (1984), no. 1, 19--26.

\bibitem{LN}
Leckband, M. A.; Neugebauer, C. J. Weighted iterates and variants of
the Hardy-Littlewood maximal operator,
{\em Trans. Amer. Math. Soc.}, {\bf 279}(1983), no. 1, 51--61.

\bibitem{MacS}
Mac\'ias, R. A. and Segovia, C.  Lipschitz functions on spaces of
homogeneous type. {\em Adv. in Math.}, {\bf 33} (1979), no. 3, 257--270.

\bibitem{Perez}
P\'erez, Carlos, Endpoint estimates for commutators of singular integral
operators, {\em J. Funct. Anal}. {\bf 128} (1995), no. 1, 163--185. 


\bibitem{Perez2}
P\'erez, C. On a theorem of Muckenhoupt and Wheeden and a weighted
inequality related to Schr\"odinger operators, {\em
Trans. Amer. Math. Soc.}, {\bf 340} (1993), no. 2, 549--562.

\bibitem{QDeng}
Qiu, D.W and Deng, D.G., The $T(1)$ theorems and commutators on spaces
of homogeneous type, 


\end{thebibliography}



\end{document} 












 













