\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{latexsym}

\usepackage[mathscr]{eucal}
\usepackage{eucal} %(with mathscr option; Euler script alphabet)
\usepackage{eufrak} % in the preambel providing the \mathfrak command
		    % for typesetting both upper and lowercase in
		    %Euler Fraktur
%\usepackage{eurosans}
%\usepackage[german]{babel}
%\usepackage[T1]{fontenc}
%\usepackage{amstex}

\def\spt{\sptilde}
\def\sph{\sphat}
%\def\eps{\varepsilon}
\def\vphi{\varphi}
\def\lam{\lambda}
\def\mf{\mathfrak}
%\def\Om{\Omega}
\def\de{\delta}
\def\sh{\sinh}
\def\ch{\cosh}
\def\th{\tanh}
%\def\F{{\cal F}}
\newcommand{\scr}{\mathscr}
\newcommand{\ud}{\mathrm{d}}

%\renewcommand{\Re}{{\mbox{Re}}}

\newtheorem{theorem}[subsection]{Theorem}
\newtheorem{lemma}[subsection]{Lemma}
\newtheorem{corollary}[subsection]{Corollary}
\newtheorem{proposition}{Propostion}

\newtheorem{remarks}[subsection]{Remarks}
\newtheorem{definition}[subsection]{Definition}

%\include{psfig}

\title{Weak type estimates of nonconvolution operators on certain Riemannian symmetric spaces 
}

\author{Shijun Zheng \thanks{Suppoted in part by NSF}\\
        {\normalsize{\sl Department of Mathematics }} \\
        {\normalsize{\sl University of Maryland }}\\
        {\normalsize{\sl College Park, MD 20742}}\\
       szheng@math.umd.edu\\
http://www.math.umd.edu$/^{\begin{tiny}\sim \end{tiny}}$szheng\\  
 %{\normalsize {USA}}\\
}
%\date{}
%\email{szheng@math.umd.edu}

%\urladdr{http://www.math.umd.edu/\sptilde szheng}
%\thanks{thanks}

%and\\      
%\author{Jianming Liu\\
%    {\normalsize {\sl Department of Mathematics }} \\
%        {\normalsize {\sl Beijing University}}\\
%        {\normalsize {\sl Beijing, }}\\
%        {\normalsize {\sl China, P.R.}}\\   
%        }

\begin{document}
\maketitle
%\tableofcontents

Keywords: Semisimple Lie groups, symmetric spaces, Bochner-Riesz
means, Jacobi transforms, Hardy spaces

MSC2000: {Primary:43A15, 43A85;  Secondary:22E30}

%\tableofcontents

\vspace{0.4in}
\begin{abstract}
Consider the Jacobi function $\phi_\lambda(t)$ of order $(\alpha,\beta)$ $(\alpha\neq-1,-2,\cdots)$; the Jacobi transform is defined by $${\widehat
f(\lambda)=\int_0^\infty f(t)\phi_\lambda(t) \Delta(t)dt},$$ where $\Delta(t)=(2\sinh t)^{2\alpha+1} (2\cosh t)^{2\beta+1}$. There is a convolution product
associated to the Jacobi transform which has the property that
$\widehat{f*g}(\lambda)=\widehat f (\lambda) \,\widehat g(
\lambda)$. % Set $\chi_r=(1/|[0,r]|)\chi_{[-r,r]}$, where for any set
	   % $A, |A|=\int_A \Delta(t)dt$. With this, a
	   % Hardy-Littlewood maximal operator can be defined as $Mf(t)=\sup_{r>0}\chi_r*|f|(t)$. 

Let $G$ be a noncompact semisimple Lie group. The Riesz means on the
homogeneous spaces $G/H$ can be defined via a weighted Jacobi transform. Based on an explicit formula 
for the kernel of the Riesz means, we obtain a weak type
estimate for the corresponding maximal operator.  
We also study the boundedness result for the Hardy spaces on $G/H$ by an
atomic decomposition adapted to $G$.

%The weak-type $(1,1)$ estimate $$|\{Mf>\lambda\}|\leq(C/\lambda)\int_0^\infty |f(t)|\Delta(t)dt$$ is shown using a covering lemma adapted to the measure $||$
%and by making estimates on the kernel $\chi_r$ and its translations. That $M$ is bounded on $L^\infty$ is straightforward; the $L^p$ estimates follow by
%interpolation.

\end{abstract}

\section{Introduction}

For $\alpha,\beta, \lam\in \mathbb{C}$, $\alpha\neq -11-2-3,\dots$,
define
$$ 
{\cal L}_{\alpha,\beta}= \frac{d}{dx^2}+ \frac{\Delta'}{\Delta}
\frac{d}{dx}, \quad x>0,$$
where $ {\Delta}(x)={\Delta}_{\alpha,\beta} =(2\sh x)^{2\alpha+1}(2\ch
x)^{2\beta+1}, x>0$. The Jacobi function $\phi_\lam $ is the unique
even $C^\infty-$ functions on $\mathbb{R}$ such that  $\phi_\lam (0)=1$
and satisfies 
$${\cal L}_{\alpha,\beta}\phi_\lam= -(\rho^2+\lam^2)\phi_\lam,$$ 
with $\rho =\alpha+\beta +1$.  For ``nice'' function $f$ define 
the Jacobi transform $\hat{f}$ by
$$ 
\hat{f}= \frac{1}{2\pi}\int_0^\infty f(t) \phi_\lam (t){\Delta}(t)dt.$$

Let $\alpha\ge \beta \ge -1/2$ and  $\alpha \neq -1/2$. If $f$ is an
even function on $\mathbb{R} $ and $s\in [0,\infty)$ the translation
$T_s$ is given by 
$$
 T_sf(t) = \int_0^\infty f(y)K(s,t,y){\Delta}(y)dy,
$$
where for $|s-t|<y<s+t $,

\begin{align}
K(s,t,y) = \frac{2^{1-2\rho}\Gamma(\alpha +1 ){(\ch s\ch t\ch y)}^{\alpha-\beta-1}}
{\sqrt{\pi}\Gamma(\alpha +1/2) ( \sh s\sh t\sh y)^{2\alpha}} \cdot\\
(1-B^2)^{\alpha-1/2}\cdot F(\alpha+\beta,\alpha-\beta; \alpha
+\frac{1}{2}, \frac{1}{2}(1-B) ),
\end{align}

and otherwise $K(s,t,y)=0$, where 
$$ B= \frac{\ch^2 s+\ch^2 t+\ch^2 y-1}{2\ch s\ch t\ch y}.$$

Note that $K$ is nonnegative, satisfying
$$
\int_0^\infty K(s,t,y )\Delta dy=1.
$$

There is a convolution given by 
$$
f* g(t)=  \int_0^\infty T_tf(s)g(t)\Delta(s)ds.$$

\begin{lemma} Define $B(x,r)$ by $B(x,r)= [x-r,x+r]$ if $x-r>0$;
$[0,x+r]:=B(x+r)$ if $t-r\neq 0$. Then 

1) If $0\neg r<\infty, 1+|B(r)| \sim (\ch r)^{2\rho}$.

2) $$ |B(r)| \sim r^{2(\alpha +1)}\quad r\le C$$

$$ |B(r)|\sim (\ch r)^{2\rho}\quad r\ge C.$$

3) For $r\le 1$, $x>2$,  $|B(x,r)| \sim r(\ch x)^{2\rho} \sim r
   e^{2\rho x} $. 

4) For $r\le 1$, $x<2$,
 $$ |B(x,r)| \sim r x^{2(\alpha +1)}\quad x\ge 2r$$

$$ |B(x,r)|\sim |B(r) |, \quad x< 2r.$$
\end{lemma}


\begin{lemma}
Let $E$ be a subset of $\mathbb{R}^+$.  $\{ B(x_k,r_k ) \}$ is a
covering of $E$ with $r_k\le 1$  for all $k$. Then there exists a
disjoint  $\{ B(x_i,r_i ) \}$ such that 
$$
|E| \le C \sum_{i=1}^\infty | B(x_i,r_i) |. 
$$
\end{lemma}

Proof similar to that of the Vitali covering lemma.


\section{Riesz means of Jacobi expansions}
(Try to write the following in terms of spectral theory)

For $z\in \mathbb{C}, \Re z \ge 0 $, we define the Bochner-Riesz means
of order $z$
by 
$$
S_R^zf(x) = \int_0^\infty (1-\frac{\lam^2+\rho^2}{R})^z_+ \hat{f}(\lam) \phi_\lam^{\alpha,\beta}
(x)|c(\lam)|^{-2}d\lam.$$

The Riesz means can be written as $S_R^zf = s_R^z * f$, here
$s_R^z $ is a function whose Jacobi transform is
$$ 
\hat{s}_R^z (\lam ) = (1-\frac{\lam^2+\rho^2}{R})^z_+.$$

Let ${\cal F}_c $ be the usual Fourier-cosine transform, ${\cal A}$
the Abel transform, then $ s_R^z={\cal A}^{-1}{\cal F}_c^{-1}(\hat{s}_R^z (\lam )).  $
Like in Koornwinder, Jacobi functions and analysis on noncompact
semisimple Lie Groups, in R.Askey et al (eds.), Special functions,
D.Reidel Publ. Com., Dordrecht. (1984?) and Giulini.S and Mauceri
G. `Almost everywhere convergence of Riesz means on certain noncompact
symmetric spaces', Ann. Mat.Pura. Appl.(4)159, (1991). We obtain

\begin{proposition} 
If $\alpha \ge \beta -1/2$,  $\alpha\neq -1/2$, then 
$$
\vert s_R^z (x)\vert \le c(z) R^{\alpha +1} ( 1+\sqrt{R} |x|)^{-Re
z-\alpha -3/2} (\frac{x}{\sh x})^{\alpha +1/2} (\frac{1}{\ch x})^{\beta +1/2}. 
$$
\end{proposition}

Consider the maximal operator
$$
S_*^zf (x)= \sup_{R>0} \vert S_R^zf (x)\vert, \quad f\in
L^p(\Delta(x)dx ), 1\le p\le 2.
$$ 

We will need the maximal function $Mf$:
$$ Mf(x)= M_{\alpha, \beta}f(x)= \sup_{r>0}\chi_r*|f|(x).$$
Here $\chi_r= \frac{1}{|B(r)|}\chi_{[-r,r]}$, $\chi_{[-r,r]}$ is the
characteristic function of $[-r,r]$.

Note. For certain discrete $\alpha, \beta$, $Mf $ has
group-theorectical interpretation as the maximal function on symmetric spaces.

\begin{theorem} Let $\alpha\ge \beta\ge -1/2$ and $\alpha \neq -1/2$,
the maximal operator $M$ has weak type $(1,1)$,
$$ \vert \{ x: Mf(x)>\lam   \}\vert \le C\lam^{-1} \Vert
f\Vert_{L^1(\Delta dx)}.$$
\end{theorem}

Define 
\begin{align}
 M_{\phi}f(x)= \sup_{t>0}\phi(t)\chi_{[-t,t]}*f(x)\\
=\sup_{t>0}\phi(t)\int_0^t T_xf(y)\Delta(y)dy.
\end{align}


\begin{theorem} Let $\alpha \ge \beta -1/2$, $\alpha\neq -1/2$. 
i) If $Re z>0$, then for $f\in L^2(\Delta(x)dx)$, 
$$ \Vert S_*^zf\Vert_2 \le c(z) \Vert f \Vert_2.$$

ii) If $Re z> \alpha +\frac{1}{2}$,   $S_*^z$ is bounded from
$L^1(\Delta(x)dx)$ to weak $L^1+L^q$ for every $q\in [4,\infty]  $. 

iii) If $Re z> (\frac{2}{p}-1)(\alpha +\frac{1}{2})$ and $1<p\le 2$,
then for every $q \ge \frac{4p}{3p-2}$, 
$$
\Vert S_*^zf\Vert_{p+q} \le c(z) \Vert f \Vert_p, \quad f\in
L^p(\mathbb{R}^+, \Delta(x)dx).
$$
\end{theorem}


Proof similar to that of Lemma 4.1 in Giulini and Mauceri, 1991.
(iii) follows from Stein's complex interpolation.

A direct corollary of the above theorem is the pointwise result.

\begin{theorem}
Let $1\le p \le 2$ and $f\in L^p(\mathbb{R}^+, \Delta(x)dx)$. If $Re z> (\frac{2}{p}-1)(\alpha +\frac{1}{2})  $,
then $\lim_{R\rightarrow \infty }  S_R^zf(x) =f(x)$ a.e.      
\end{theorem}


\vspace{0.2in}

\section{Some background in analysis on symmetric spaces}

Hardy spaces and maximal operators on real rank one semisimple Lie groups. I. (English. English summary) 
Tohoku Math. J. (2) 52 (2000), no. 1, 1--18.

G.B.Folland:

The purpose of this paper is to introduce a version of the atomic Hardy space $H^1$ on a semisimple Lie group $G$ of real rank one so that certain maximal
operators are bounded from $H^1$ to $L^1$. Specifically, let $G=K\exp {p}$ be the Cartan decomposition of $G$. Balls centered at the identity in $G$
are defined in terms of the norm $\sigma(k\exp X)=\|X\|$, where $\| \cdot\|$ is the Euclidean norm on ${ p}$ coming from the Killing form, and balls centered at
other points are left translates of these. For $1<p\le\infty$, a $(1,p,0)$-atom is a function $a$ supported in some ball $B$ of radius $r$ such that
$\|a\|_p\le|B|^{(1/p)-1}$ and $\int_G a=0$ if $r\le 1$, or $\|a\|_p\le|B|^{-1}$ if $r>1$; the space $H^1_{p,0}$ is defined to be the set of $f\in L^1(G)$ such that
$s=\sum\lambda_ia_i$, where $a_i$ is a $(1,p,0)$-atom and $\sum |\lambda_i|<\infty$. 

Given a family $\{\phi_t\}_{t>0}$ of $L^1$ functions on $G$, define the maximal operator $M_\phi^\epsilon$ for $\epsilon\ge0$ by $$M_\phi^\epsilon f(g)
=\sup_{t>0}(1+t)^{-\epsilon}|f*\phi_t(g)|.$$ The author proves that the operator $M_\phi^\epsilon$ is bounded from $H^1_{p,0}$ to $L^1(G,dg)$ and the
operator $M_\phi^0$ is bounded from $H^1_{p,0}$ to $L^1(G,\,(1+\sigma(g))^{-\epsilon} dg)$ in the following cases: (1) $\epsilon>0$, and $\phi_t$ is a family
of functions obtained from a single $K$-bi-invariant function $\phi\in C_c^\infty(G)$ by suitable dilations; (2) $\epsilon>1/2$, and $\phi_t$ is the kernel of the
heat semigroup $e^{t\Delta}$ on $G/K$; (3) $\epsilon>0$, and $\phi_t$ is the kernel of the Poisson semigroup $e^{-t\sqrt{-\Delta}}$. In all cases the proofs
depend on detailed pointwise estimates for $f*\phi_t$.

-------------------------------------------------------

Giulini, Saverio(I-GENOE); Sjögren, Peter 
A note on maximal functions on a solvable Lie group. 
Arch. Math. (Basel) 55 (1990), no. 2, 156--160.

The paper is closely related to one by  G. Gaudry, Giulini and
A. M. Mantero%\en 
\ref[Tôhoku Math. J. (2) 42 (1990), no. 2, 195--203; see the preceding review]. Here maximal functions on the
group "$ax+b$" of the form $$M^\psi f(x,y)=\sup_{\rho>0}|R^\psi_\rho(x,y)|^{-1}\int_{R^\psi_\rho(x,y)} |f(x',y')|\,dx'\,dy',$$ where $R^\psi_\rho(x,y)=\{(x',y')\in\bold R\:|x'-x|<\rho$,
$|y'-y|<e^x\psi(\rho)\}$, are studied. The main theorem of the paper is that if $\psi(\rho)=\rho^\alpha$, then $M^\psi$ is not of weak type $(1,1)$. Also, if $\psi(\rho)=e^{\beta\rho}$, then $M^\psi$
is of weak type $(1,1)$ if and only if $\beta>1$. The proof is very illuminating.

                                    Reviewed by A. Hulanicki 

--------------------------------------------------------------

Giulini, Saverio; Mauceri, Giancarlo; Meda, Stefano $L\sp p$ multipliers on noncompact symmetric spaces. J. Reine Angew. Math. 482 (1997), 151--175. (Reviewer: Tomasz
  Przebinda) 
 

Recall that a Fourier multiplier on $L^p(\bold R^n)$, $1\leq p<\infty$, is the Fourier transform $\widehat u$ of a tempered distribution $u$ on $\bold R^n$ such that the convolution operator $f\to
f*u$ is bounded on $L^p(\bold R^n)$. 

For $p=2$, the Fourier multipliers are simply bounded functions on $\bold R^n$. The problem of characterization of Fourier multipliers for $p\ne 2$ has been investigated by many prominent classical
harmonic analysts, and remains open. 

Let $G$ be a noncompact connected semisimple Lie group with finite center. Let $K\subseteq G$ be a maximal compact subgroup and let $G=KAN$ be an Iwasawa decomposition of $G$. Recall
that the space of $K$-bi-invariant absolutely integrable functions on $G$ is a commutative Banach algebra. The spectrum of this algebra is described in terms of (bounded) spherical functions on
$G$: $$ \phi_{\lambda}(x)=\int_Ke^{i(\lambda -\rho)(H(xk))}\,dk \qquad
(x\in G, \lambda\in 
\mathfrak{ a}_{\bold C}^*), $$ where $\mathfrak{ a}_{\bold C}^*$ is the complexified dual of the Lie algebra $\mathfrak{ a}$
of the group $A$, and $x\in K\,exp(H(x))\,N$. Thus the Gel'fand
transform of a 
$K$-bi-invariant absolutely integrable function $f$ on $G$ can be written as $$ \tilde f(\lambda) = \int_G
f(x)\,\phi_{-\lambda}(x)\,dx \qquad (\lambda \in \mathfrak{ a}_{\bold
C}^*) $$ 
and is called the spherical Fourier transform of $f$. (Here we take only those $\lambda$ for which the $\phi_{-\lambda}$ is
bounded.) If $\lambda\in \mathfrak{ a}^*$, then the above formula makes sense for any tempered distribution $f$ on $G$. (These distributions have been defined by Harish-Chandra.) 

Let $X=G/K$. One identifies functions on $X$ with functions on $G$ invariant under right translations by $K$. In analogy to the classical situation one defines a spherical multiplier on $L^p(X)$,
$1\leq p <\infty$, to be the spherical Fourier transform $\tilde u$ of a $K$-bi-invariant tempered distribution $u$ on $G$ such that the convolution operator $f\mapsto f*u$ is bounded on
$L^p(X)$. 

Let $\rho\in \mathfrak{ a}^*$ denote one half times the sum of roots
of $\mathfrak{ a}$ 
in $\mathfrak{ n}$, the Lie algebra of $N$. Let $W$ be the Weyl group
of 
$(\mathfrak{ g}, \mathfrak{ a})$. For $t>0$ let $W_t$ be the
interior of the convex hull in $\mathfrak{ a}^*$ of the $W$ orbit of
$t \rho$. Let 
$T_t=\mathfrak{ a}^*+i W_t$. Harish-Chandra's work implies easily that, as in the classical situation, a spherical multiplier on
$L^2(X)$ is a bounded function on $\mathfrak{ a}^*$. J.-L. Clerc and
E. M. Stein 
\ref[Proc. Nat. Acad. Sci. U.S.A. 71 (1974), 3911--3912] have shown that if $p\ne 2$ then a spherical
multiplier on $L^p(X)$ extends to a bounded holomorphic function on the tube $T_{|2/p-1|}$. For $G$ complex they also gave a sufficient condition: if $m$ is a $W$-invariant holomorphic
function on the tube $T_{|2/q-1|}$, $1<q<2$, whose derivatives up to order $\dim\,X/2 +1$ satisfy decay conditions of Mikhlin-Hörmander type, then $m$ is a spherical multiplier on $L^p(X)$ for
$q\leq p\leq q'$, where $q'$ is the conjugate exponent to $q$. This last result is generalized in the paper under review. The main result is (roughly) as follows. 

For a bounded holomorphic function $M$ on the tube $T_t$, and $\eta$ 
in the closure of $W_t$, let $M_\eta(\lambda)=M(\lambda+i\eta) (\lambda \in \mathfrak{ a}^*)$ be the non-tangential limit of $M$.
Let $c$ denote the Harish-Chandra $c$-function on $\mathfrak{ a}^*$. Theorem: Let $G$ be complex. Let $m$ be a $W$-invariant holomorphic function on the tube $T_1$. Then the following hold. (i)
If $m$ is bounded in $T_1$ and the function ${\cal S}m$ defined by the rule $$ {\cal S}m(\lambda)=\sum_{s\in W} (\det\,s)\, (c^{-1}m)_{s\rho}(\lambda)\qquad (\lambda\in \mathfrak{ a}^*) $$ is a Fourier
multiplier on $L^p(\mathfrak{ a})$ for some $1<p<\infty$, then $m$ is a spherical Fourier multiplier on $L^p(X)$, and the norm of $m$ can be dominated by the norm of ${\cal S}m$. (ii) Let
$\omega(\lambda)=\break (\langle \lambda, \lambda\rangle +4\langle
\rho, \rho\rangle)^{(n-l)/4}$, where $n=\dim\,X$ and
$l=\dim\,\mathfrak{ a}$. If $\omega m$ is a Fourier multiplier on 
$L^p(\mathfrak{ a})$
uniformly in every proper subtube of $T_1$ for all $1<p<\infty$, then $m$ is a spherical Fourier multiplier on $L^p(X)$ for all $1<p<\infty$. 

The authors prove an analogous theorem for $X$ of rank one ($\dim \mathfrak{ a} =1$) and for radial multipliers on free groups.

                                   Reviewed by Tomasz Przebinda 

                                       [References]

   1.J.-Ph. Anker, Sharp estimates for some functions of the Laplacian on noncompact symmetric spaces, Duke Math. J. 65 (1992), 257--297. MR 93b:43007 
   2.J.-Ph. Anker, $L^p$ Fourier multipliers on Riemannian symmetric spaces of the noncompact type, Ann. Math. 132 (1990), 597--628. MR 92e:43006 
   3.J.-P. Anker and N. Lohoué, Multiplicateurs sur certains espaces symétriques, Amer. J. Math. 108 (1986), 1303--1354. MR 88c:43008 
   4.A. Baernstein II and T. Sawyer, Embedding and multiplier theorems for $H^p( R^n)$, Mem. Amer. Math. Soc. 318 (1985), 1--82. MR 86g:42036 
   5.J.L. Clerc, Transformation de Fourier sphérique des espaces de Schwartz, J. Funct. Anal. 37 (1980), 182--202. MR 81j:22016 
   6.J.L. Clerc and E.M. Stein, $L^p$ multipliers for noncompact symmetric spaces, Proc. Nat. Acad. Sci U.S.A. 71 (1974), 3911--3912. 
   7.M.G. Cowling, Harmonic analysis on semigroups, Ann. Math. 117 (1983), 267--283. MR 84h:43004 
   8.M.G. Cowling, S. Giulini and S. Meda, $L^p - L^q$ estimates for functions of the Laplace-Beltrami operator on noncompact symmetric spaces. I, Duke Math. J. 72 (1993), 109--150. MR
    95b:22031 
   9.M.G. Cowling, S. Giulini and S. Meda, $L^p - L^q$ estimates for functions of the Laplace-Beltrami operator on noncompact symmetric spaces. III, preprint. 
  10.P. Eymard, Algèbres $A_p$ et convoluteurs de $L^p$, Sem. Bourbaki 367, November 1969. 
  11.A. Figà-Talamanca and M. Picardello, Harmonic Analysis on Free Groups, Lect. Notes Pure Appl. Math. 87, Marcel Dekker, 1983. MR 85j:43001 
  12.R. Gangolli, On the Plancherel formula and the Paley-Wiener theorem for spherical functions on semisimple Lie groups, Ann. Math. 93 (1971), 150--165. MR 44 
  13.P. Graczyk and J.-J. Loeb, Bochner and Schoenberg theorems on symmetric spaces in the complex case, Bull. Soc. Math. France 122 (1994), 571--590. MR 95m:43008 
  14.S. Helgason, Groups and Geometric Analysis, Academic Press, New York 1984. MR 86c:22017 
  15.C.S. Herz, Le rapport entre l'algèbre $A_p$ d'un groupe et d'un sous-groupe, C.R. Acad. Sc. Paris 271 (1970), 244--246. 
  16.L. Hörmander, Estimates for translation invariant operators in $L^p$ spaces, Acta Math. 104 (1960), 93--140. 
  17.L. Hörmander, The Analysis of Linear Partial Differential Operators, Vol. I, Springer Verlag, Berlin 1983. 
  18.C. Meaney, Transferring estimates for zonal convolution operators, Anal. Math. 15 (1989), 175--193. MR 91g:43004 
  19.R.J. Stanton and P.A. Tomas, Expansions for spherical functions on noncompact symmetric spaces, Acta Math. 140 (1978), 251--276. 
  20.E.M. Stein and G. Weiss, Introduction to Fourier Analysis on Euclidan Spaces, Princeton University Press, Princeton N.J. 1971. 
  21.M. Taylor, $L^p$ estimates on functions of the Laplace operator, Duke Math. J. 58 (1989), 773--793. MR 91d:58253 
  22.G.N. Watson, A Treatise on the Theory of Bessel Functions, Cambridge Univ. Press, London 1962. 


-------------------------------------------------------------------

De Michele, Leonede(I-MILAN); Mauceri, Giancarlo(I-GENO) 
$H\sp p$ multipliers on stratified groups. 
Ann. Mat. Pura Appl. (4) 148 (1987), 353--366.

Suppose $G$ is a stratified Lie group of homogeneous dimension $Q$,
${\cal L}$ 
is a sub-Laplacian on $G$, and $M$ is a bounded Borel function on $(0,\infty)$.  A. Hulanicki and  E. M.
Stein \ref[see the reviewer and Stein, Hardy spaces on homogeneous groups, Princeton Univ. Press, Princeton, N.J., 1982; MR 84h:43027] proved that the operator $M({\cal L})$ is bounded on
$H^p(G)$ for $Q/(Q+r)<p<\infty$, and in particular on $L^p(G)$ for $1<p<\infty$, provided that $M$ is of class $C^{(s)}$ and $|t^jM^{(j)}(t)|\le C$ for $j\le s$ where $s>r+(3Q/2)+2$. The
authors obtain the same conclusion under the weaker hypothesis that $M$ satisfies an appropriate Lipschitz-Besov condition of order $s$ where $s>r+(Q/2)+1$. This hypothesis is nearly optimal;
when $G=\bold R^n$ the sharp condition on $s$ is known to be $s>r+(n/2)$. The proof exploits the atomic and molecular characterizations of $H^p$ spaces.

                                   Reviewed by Gerald B. Folland 


-----------------------------------------

Ionescu, Alexandru D. 
A maximal operator and a covering lemma on non-compact symmetric spaces. (English. English summary) 
Math. Res. Lett. 7 (2000), no. 1, 83--93.

Let $G$ be a connected semisimple group, $K\subseteq G$ a maximal compact subgroup and $X=G/K$ the corresponding
non-compact symmetric space. Let ${\cal F}$ denote the set of all balls in $X$ (with all possible centers and radii). For a
locally integrable function $f$ on $X$, let $$ \mathscr{ M}_{\mathscr{
F}}f(z)=
\underset{z\in B\in \mathscr{ F}}\to{\sup} \frac{1}{|B|}
\int_B|f(x)|\,dx \qquad (z\in X), $$ where $|B|$ denotes the volume of the ball $B$. The main result of this work is a
theorem which states that the maximal operator $\mathscr{ M}_{\mathscr{ F}}: L^p(X)\to L^p(X)$ is bounded in the (sharp) range
$p\in (2,\infty]$.

                       Reviewed by Tomasz Przebinda 

                            [References]

   1.J.L. Clerc and E.M. Stein, $L^p$- multipliers for noncompact symmetric spaces, Proc. Natl. Acad. Sci. U.S.A. 71 (1974),
    3911--3912. 
   2.A. Cordoba and R. Fefferman, A geometric proof of the strong maximal theorem, Ann. Math. 102 (1975), 95--100.  
   3.S. Helgason, Geometric analysis on symmetric spaces, Mathematical Surveys and Monographs, 39, American
    Mathematical Society, Providence, RI, 1994. MR 96h:43009 
   4.A.D. Ionescu, An endpoint estimate for the Kunze-Stein phenomenon and related maximal operators, preprint 1999. cf. CMP
    1792296 
   5.P. Sjögren, Admissible convergence of Poisson integrals in symmetric space, Ann. Math. 124 (1986), 313--335. MR
    88g:43008 
   6.E.M. Stein and G. Weiss, Introduction to Fourier analysis on Euclidean spaces, Princeton Mathematical Series, No. 32,
    Princeton University Press, Princeton, N.J., 1971. 
   7.J.O.Strömberg, Weak type $L^1$ estimates for maximal functions on noncompact symmetric spaces, Ann. Math. 114
    (1981), 115--126. MR 82k:43010 

-------------------------------------

Ionescu, Alexandru D.(1-PRIN) 
An endpoint estimate for the Kunze-Stein phenomenon and related maximal operators. (English. English summary)

Ann. of Math. (2) 152 (2000), no. 1, 259--275.

Let $G$ be a noncompact connected semisimple Lie group, of real rank one with finite center, and let $L^{p,q}(G)$
denote the Lorentz space relative to the Haar measure on $G$. The author proves that $$ L^{2,1}(G) * L^{2,1}(G)
\subseteq L^{2,\infty}(G). $$ Next, let $K\subseteq G$ be a maximal compact subgroup of $G$ and $X=G/K$ the
corresponding symmetric space. For a function $f$ on $X$, 
let $$ \mathscr{ M} f(z)=\sup_{B \ni z} {{1}\over{\vert B\vert }}
\int_B | f(x)| \,dx \qquad (z\in X), $$ where $\vert B\vert$ denotes the volume of the ball $B$. The author proves that $\scr{M}$ is a bounded operator from $L^{2,1}(X)$ to $L^{2,\infty}(X)$ and from $L^p(X)$ to $L^p(X)$ in the sharp range $p\in
(2,\infty]$. He also notes that $\scr{ M}$ is not bounded from $L^{2,u}(X)$ to $L^{2,v}(X)$ unless $u=1$ and $v=\infty$. 

Remarkably, the proofs of the above results are based only on real variable techniques. These real variable techniques
open up many new possibilities for research in the area.

                         Reviewed by Adam Sikora 

                            [References]

   1.J.-Ph. Anker, $L_p$ Fourier multipliers on Riemannian symmetric spaces of the noncompact type, Ann. of Math.
    132 (1990), 597--628. MR 92e:43006 
   2.A. Cordoba and R. Fefferman, A geometric proof of the strong maximal theorem, Ann. of Math. 102 (1975), 95--100.
     
   3.M. Cowling, The Kunze-Stein phenomenon, Ann. of Math. 107 (1978), 209--234. 
   4.M. Cowling, Herz's "principe de majoration" and the Kunze-Stein phenomenon, in Harmonic Analysis and Number
    Theory (Montreal, PQ, 1996), 73--88, CMS Conf. Proc. 21, A.M.S., Providence, RI, 1997. MR 98k:22040 
   5.J.-L. Clerc and E. M. Stein, $L^p$-multipliers for noncompact symmetric spaces, Proc. Natl. Acad. Sci. USA 71
    (1974), 3911--3912. 
   6.S. Helgason, Geometric Analysis on Symmetric Spaces, A.M.S., Providence, RI, 1994. MR 96h:43009 
   7.A. D. Ionescu, A maximal operator and a covering lemma on non-compact symmetric spaces, Math. Res. Lett. 7
    (2000), 83--93. MR 2001g:43013 
   8.T. H. Koornwinder, Jacobi functions and analysis on noncompact semisimple Lie groups, in Special Functions: Group
    Theoretical Aspects and Applications, 1--85, Math. Appl. Reidel, Dordrecht-Boston, MA, 1984. MR 86m:33018 
   9.N. Lohoué and T. Rychener, Some function spaces on symmetric spaces related to convolution operators, J.
    Funct. Anal. 55 (1984), 200--219. MR 85d:22024 
  10.R. A. Kunze and E. M. Stein, Uniformly bounded representations and harmonic analysis of the $2 \times 2$
    unimodular group, Amer. J. Math. 82 (1960), 1--62.  
  11.E. M. Stein and G. Weiss, Introduction to Fourier Analysis on Euclidean Spaces, Princeton Math. Series, No. 32, Princeton
    Univ. Press, Princeton, NJ, 1971. 
  12.J.-O. Strömberg, Weak type $L^1$ estimates for maximal functions on noncompact symmetric spaces, Ann. of Math.
    114 (1981), 115--126. MR 82k:43010 
  13.N. J. Weiss, Fatou's theorem for symmetric spaces, in Symmetric Spaces (Short Courses, Washington Univ., St.
    Louis, MO, 1969--1970), 413--441, Pure and Appl. Math. 8, Marcel Dekker, New York, 1972. 

-----------------------------------------------------------

Ionescu, Alexandru D.(1-IASP-SM) 
Singular integrals on symmetric spaces of real rank one. (English. English summary) 
Duke Math. J. 114 (2002), no. 1, 101--122.

Let $\Bbb{G}$ be a noncompact connected semisimple Lie group with finite center, let $\Bbb{K}$ be a maximal compact
subgroup of $\Bbb{G}$ and let $\Bbb{X}=\Bbb{G}/\Bbb{K}$ be an associated symmetric space. Let $K(g)$ be a
$K$-bi-invariant function on $\Bbb{G}$ (that is $K(k_1gk_2)=K(g) \forall k_1,k_2\in \Bbb{K}$) and let $$ T\colon
f(x)\mapsto K*f(x)=\int_\Bbb{G} K(g)\,f(g^{-1}x)\,dg, \quad x\in\Bbb{X}, g\in\Bbb{G}, $$ be the convolution operator
defined by the kernel $K(g)$. In the paper under review the author obtains new sufficient conditions for
$L^p(\Bbb{X})$-boundedness of operator $T$ if $\Bbb{X}$ is a symmetric space of rank one (a so-called new
transference principle and a new variant of the Herz majorizing principle). As an application, the author proves
$L^p$-boundedness of operators defined by Fourier multipliers which satisfy singular differential inequalities of the
Hörmander-Michlin type. He also finds sharp bounds on the $L^p$-norm of large imaginary powers of the critical
$L^p$-Laplacian.

                        Reviewed by Sergei S. Platonov 

                            [References]

   1.J.-P. Anker, $L_p$ Fourier multipliers on Riemannian symmetric spaces of the noncompact type, Ann. of Math. (2) 132
    (1990), 597--628. MR 92e:43006 
   2.J.-P. Anker, Sharp estimates for some functions of the Laplacian on noncompact symmetric spaces, Duke Math. J. 65
    (1992), 257--297. MR 93b:43007 
   3.J.-P. Anker and N. Lohoué, Multiplicateurs sur certains espaces sym\'etriques, Amer. J. Math. 108 (1986), 1303--1353.
    MR 88c:43008 
   4.J.-P. Anker and A. Seeger, Spectral multipliers of noncompact Riemannian manifolds, preprint, 1999. 
   5.J.-L. Clerc and E. M. Stein, $L^p$- multipliers for noncompact symmetric spaces, Proc. Nat. Acad. Sci. U.S.A. 71
    (1974), 3911--3912. 
   6.R. R. Coifman and G. Weiss, Transference Methods in Analysis, CBMS Regional Conf. Ser. in Math. 31, Amer. Math.
    Soc., Providence, 1976. 
   7.M. Cowling, The Kunze-Stein phenomenon, Ann. of Math. (2) 107 (1978), 209--234. 
   8.M. Cowling, "Herz's `principe de majoration' and the Kunze-Stein phenomenon" in Harmonic Analysis and Number
    Theory (Montreal, 1996), CMS Conf. Proc. 21, Amer. Math. Soc., Providence, 1997, 73--88. MR 98k:22040 
   9.M. Cowling, S. Giulini, and S. Meda, $L^p\text{-}L^q$ estimates for functions of the Laplace-Beltrami operator on
    noncompact symmetric spaces, I, Duke Math. J. 72 (1993), 109--150. MR 95b:22031 
  10.C. Fefferman and E. M. Stein, $H^p$ spaces of several variables, Acta Math. 129 (1972), 137--193.
  11.S. Giulini, G. Mauceri, and S. Meda, $L^p$ multipliers on noncompact symmetric spaces, J. Reine Angew. Math. 482
    (1997), 151--175. MR 98g:43006 
  12.S. Helgason, Geometric Analysis on Symmetric Spaces, Math. Surveys Monogr. 39, Amer. Math. Soc., Providence,
    1994. MR 96h:43009 
  13.C. Herz, Sur le ph\'enom\`ene de Kunze-Stein, C. R. Acad. Sci. Paris Sér. A-B 271 (1970), A491--A493.
  14.A. D. Ionescu, Fourier integral operators on noncompact symmetric spaces of real rank one, J. Funct. Anal. 174 (2000),
    274--300. MR 2001h:43009 
  15.A. W. Knapp and E. M. Stein, Intertwining operators for semisimple groups, Ann. of Math. (2) 93 (1971), 489--578. 
  16.R. A. Kunze and E. M. Stein, Uniformly bounded representations and harmonic analysis of the $2 \times 2$ real unimodular
    group, Amer. J. Math. 82 (1960), 1--62. 
  17.N. Lohoué, Puissances complexes de l'op\'erateur de Laplace-Beltrami, C. R. Acad. Sci. Paris Sér. A-B 290 (1980),
    A605--A608. MR 81h:58062 
  18.N. Lohoué, Estim\'ees de type Hardy pour l'op\'erateur $\Delta + \lambda$ d'un espace sym\'etrique de type non compact, C.
    R. Acad. Sci. Paris Sér. I Math. 308 (1989), 11--14. MR 90d:43008 
  19.N. Lohoué and T. Rychener, Some function spaces on symmetric spaces related to convolution operators, J. Funct. Anal.
    55 (1984), 200--219. MR 85d:22024 
  20.R. J. Stanton and P. A. Tomas, Expansions for spherical functions on noncompact symmetric spaces, Acta Math. 140
    (1978), 251--276. 
  21.E. M. Stein, Singular Integrals and Differentiability Properties of Functions, Princeton Math. Ser. 30, Princeton Univ. Press,
    Princeton, 1970.  
  22.E. M. Stein, Harmonic Analysis: Real-Variable Methods, Orthogonality, and Oscillatory Integrals, Princeton Math. Ser. 43,
    Monogr. Harmon. Anal. 3, Princeton Univ. Press, Princeton, 1993. MR 95c:42002 
  23.J.-O. Strömberg, Weak type $L^1$ estimates for maximal functions on noncompact symmetric spaces, Ann. of Math. (2)
    114 (1981), 115--126. MR 82k:43010 
  24.M. E. Taylor, $L^p$- estimates on functions of the Laplace operator, Duke Math. J. 58 (1989), 773--793. MR
    91d:58253 
-------------------------------------------------------

Ionescu, Alexandru D.(1-PRIN) 
Fourier integral operators on noncompact symmetric spaces of real rank one. (English. English summary) 
J. Funct. Anal. 174 (2000), no. 2, 274--300.

This paper contains two theorems in harmonic analysis on rank-one Riemannian symmetric spaces. Theorem A concerns
$L^p$-boundedness for Fourier multipliers of the form $m(\lambda)\cos(\lambda \tau)$ and $m(\lambda)
(\lambda^2+\rho^2)^{1/2} \lambda^{-1}\sin(\lambda \tau)$, with $m$ a $(1-n)·|1/2-1/p|$ symbol on the $L^p$-tube. As a
corollary, the author obtains a sharp (as regards to the Sobolev spaces involved) $L^p$-estimate for solutions of the
wave equation. Theorem B deals with $L^p$-boundedness for the analogue to Stein's maximal spherical operator. 

The main new idea in the paper, I believe, is the introduction of a BMO space, used in the proof of Theorem A. The
definition is local in the sense that the supremum is taken only over balls with radius less than or equal to 1.
Surprisingly, the author is able to show that this space can be used as an endpoint space for interpolation to give
$L^p$-bounds. I think it is likely that this space will be useful also in the study of other problems. (Atomic Hardy spaces
were introduced earlier by T. Kawazoe \ref[Japan. J. Math. (N.S.) 11 (1985), no. 2, 293--343; MR 88g:43006].) An
important reference that seems to be missing in the paper is \ref[S. Giulini, G. Mauceri and S. Meda, J. Reine Angew.
Math. 482 (1997), 151--175; MR 98g:43006].

                        Reviewed by Andreas Nilsson 

                            [References]

   1.J. Ph. Anker, $L^p$ Fourier multipliers on Riemannian symmetric spaces of the noncompact type, Ann. of Math. 132
    (1990), 597--628. MR 92e:43006 
   2.J. Ph. Anker and N. Lohoué, Multiplicateurs sur certains espaces symétriques, Amer. J. Math. 108 (1986),
    1303--1354. MR 88c:43008 
   3.J. Bourgain, Averages in the plane over convex curves and maximal operators, J. Anal. Math. 47 (1986), 69--85.
    MR 88f:42036 
   4.W. O. Bray, Aspects of harmonic analysis on real hyperbolic space, in "Lecture Notes in Pure and Appl. Math.,"
    Vol. 157, pp. 77--102, Dekker, New York, 1994. MR 95k:43008 
   5.J. L. Clerc and E. M. Stein, $L^p$-multipliers for noncompact symmetric spaces, Proc. Nat. Acad. Sci. U.S.A. 71
    (1974), 3911--3912.
   6.M. Cowling, S. Giulini, and S. Meda, $L^p - L^q$ estimates for functions of the Laplace-Beltrami operator on
    noncompact symmetric spaces, I, Duke Math. J. 72 (1993), 109--150. MR 95b:22031 
   7.C. Fefferman and E. M. Stein, $H^p$ spaces of several variables, Acta Math. 129 (1972), 137--193. 
   8.S. Giulini and S. Meda, Oscillating multipliers on noncompact symmetric spaces, J. Reine Angew. Math. 409 (1990),
    93--105. MR 91j:43010 
   9.S. Helgason, "Geometric Analysis on Symmetric Spaces," Amer. Math. Soc., Providence, RI, 1994. MR 96h:43009
  10.A. E. Kohen, Maximal operators on hyperboloids, J. Operator Theory 3 (1980), 41--56. MR 81j:43020 
  11.N. Lohoué, Puissance complexes de l'opérateur de Laplace-Beltrami, C. R. Acad. Sci. Paris S\'er. A 290 (1980),
    605--608. MR 81h:58062 
  12.N. Lohoué, Estimées $L^p$ des solutions de l'équation des ondes sur les variétés riemanniennes, les groupes de
    Lie et applications, in "Harmonic Analysis and Number Theory, Montreal, PQ, 1996," CMS Conf. Proc., Vol. 21,
    pp. 103--126, Amer. Math. Soc., Providence, 1996. MR 98j:58120 
  13.J. Peral, $L^p$ estimates for the wave equation, J. Funct. Anal. 36 (1980), 114--145. MR 81k:35089 
  14.A. Seeger, C. D. Sogge, and E. M. Stein, Regularity properties of Fourier integral operators, Ann. of Math. 134
    (1991), 231--251. MR 92g:35252 
  15.C. D. Sogge, Propagation of singularities and maximal functions in the plane, Invent. Math. 104 (1991), 349--376.
    MR 92i:58192 
  16.C. D. Sogge and E. M. Stein, Averages over hypersurfaces: Smoothness of generalized Radon transforms, J. Anal.
    Math. 54 (1990), 165--188. MR 91i:58145 
  17.R. J. Stanton and P. A. Tomas, Expansions for spherical functions on noncompact symmetric spaces, Acta Math.
    140 (1978), 251--271. 
  18.E. M. Stein, Maximal functions: Spherical means, Proc. Nat. Acad. Sci. U.S.A. 73 (1976), 2174--2175. 
  19.E. M. Stein, "Harmonic Analysis," Princeton Univ. Press, Princeton, NJ, 1993. MR 95c:42002 
  20.D. Tataru, Strichartz estimates in the hyperbolic space and global existence for the semilinear wave equation,
    preprint, 1997. cf. CMP 1804518 
  21.E. C. Titchmarsh, "The Theory of Functions," 2nd ed., Oxford Univ. Press, London, 1939. 
--------------------------------------------------------------

Ionescu, Alexandru D.(1-IASP-SM) 
On the Poisson transform on symmetric spaces of real rank one. (English. English summary) 
J. Funct. Anal. 174 (2000), no. 2, 513--523.

For an arbitrary locally integrable function $F$ on a real rank-one symmetric space $X=G/K$, the following norm is
defined: $$M(F)=\left(\limsup_{R\to\infty}\int_{B(\bold 0,R)}|F(z)|^2dz\right)^{1\over 2},$$ where $dz$ is a suitable
normalized $G$-invariant measure on $X$ and $\bold 0=eK$ is the origin of $X$. 

Let $G=KAN$ be the Iwasawa decomposition of the group $G$ and let $\lambda\in (\log A)^*_{\bold C}$. The Poisson
transform ${\scr P}_\lambda$ associates to an arbitrary integrable function $f$ on the boundary $B=K/M$ of $X$ a
function on $X$ according to the formula $${\scr P}_\lambda f(z)=\int_{K/M}e^{(i\lambda+\rho)A(z,b)}f(b)db,$$ where $db$
is the normalized $K$-invariant measure on $B$ and $\exp(-A(gK,kM))$ is the $A$-component in the Iwasawa
decomposition of $g^{-1}k$. 

The principal result of the paper states that for every real $\lambda\neq 0$, the Poisson transform establishes a bijection
between $L^2(B)$ and the space $${\scr E}^2_\lambda(X)=\{F\in{\scr E}(X)|\,\Delta
F=-(|\lambda|^2+|\rho|^2)F\quad\text{and}\quad M(F)<\infty\},$$ where $\Delta$ is the Laplacian on $X$,
$|\lambda|=|\lambda(H_0)|$, $|\rho|=|\rho(H_0)|$ and $H_0$ is a suitably chosen fixed element of $\log A$. 

Moreover, one obtains a Plancherel-type formula: $$M({\scr P}_\lambda f)=C_0|\text c(\lambda)|·\|f\|_{L^2(B)}.$$

                       Reviewed by Antoni Wawrzynczyk 

                            [References]

   1.W. O. Bray, Aspects of harmonic analysis on real hyperbolic space, in "Lecture Notes in Pure and Appl. Math.,"
    Vol. 157, pp. 77--102, Dekker, New York, 1994. MR 95k:43008 
   2.S. Helgason, Eigenspaces of the Laplacian; integral representations and irreducibility, J. Funct. Anal. 17 (1974),
    328--353. 
   3.S. Helgason, "Geometric Analysis on Symmetric Spaces," Amer. Math. Soc., Providence, RI, 1994. MR 96h:43009
   4.M. Kashiwara, A. Kowata, K. Minemura, K. Okamoto, T. Oshima, and M. Tanaka, Eigenfunctions of invariant
    differential operators on a symmetric space, Ann. of Math. 107 (1978), 1--39. MR 81f:43013 
   5.A. W. Knapp and E. M. Stein, Intertwining operators for semisimple groups, Ann. of Math. 93 (1971), 489--578. 
   6.N. Lohoué and T. Rychener, Some function spaces on symmetric spaces related to convolution operators, J.
    Funct. Anal. 55 (1984), 200--219. MR 85d:22024 
   7.P. Sjögren, Characterizations of Poisson integrals on symmetric spaces, Math. Scand. 49 (1981), 229--249. 
  
   8.R. J. Stanton and P. A. Tomas, Expansions for spherical functions on noncompact symmetric spaces, Acta Math.
    140 (1978), 251--271. 
   9.E. M. Stein, "Harmonic Analysis," Princeton Univ. Press, Princeton, NJ, 1993. MR 95c:42002 
  10.R. S. Strichartz. Harmonic analysis as spectral theory of Laplacians, J. Funct. Anal. 87 (1989), 51--148. MR
    91c:43015 
  11.R. S. Strichartz, Corrigendum to "Harmonic analysis as spectral theory of Laplacians", J. Funct. Anal. 109 (1992),
    457--460. MR 93j:43016 

-------------------------------------------------

\vspace{.4in}

Kawazoe, Takeshi(J-KEIOES) 
A characterization of the Poisson kernel on the classical real rank one symmetric spaces. 
Tokyo J. Math. 15 (1992), no. 2, 365--379.


Introduction: "Let $G$ be a connected real rank-one semisimple Lie
group and $G=KAN$ an Iwasawa decomposition 
for $G$. Let $\mathfrak{g}=\mf{ k}+\mf{a}+\mf{ n}$ denote the corresponding Iwasawa decomposition for the Lie algebra $\mf{ g}$ of $G$. We define $H(x)$ $(x\in G)$ as the unique element in
$\mf{ a}$ such that $x\in K\exp H(x)N$ and put $\rho(H)={\rm tr}({\rm
ad}(H)\vert \sb \mf{ n})$ for $H\in\mf{ a}$. 
Let $M$ be the centralizer of $A$ in $K$
and $\Delta$ the Laplace-Beltrami operator on $G/K$. Then the Poisson kernel $P\colon G/K\times K/M\to\bold R$ is given by
$P(gK,kM)=\exp(-2\rho(H(g\sp {-1}k)))$, and for each $s\in\bold C$, $P\sp s$ is an eigenfunction of $\Delta$ with eigenvalue $\lambda\sb s$, say. Then our
problem can be stated as follows. Problem: Let us suppose that a real-valued, $C\sp 2$ function $F$ on $G/K$ satisfies the following conditions: (1) $\Delta
F=0$, (2) $\Delta F\sp 2=\lambda\sb 2F\sp 2$, (3) $F(eK)=1$. Then is $F$ determined by $F(gK)=P(gK,kM)$ for an element $kM$ in $K/M$? 

"When $G={\rm SO}\sb 0(n,1)$ and ${\rm SU}(n,1)$, affirmative answers were obtained elsewhere [M. Chipot, P. Eymard and T. Tahani, in Symposia
Mathematica, Vol. XXIX (Cortona, 1984), 111--129, Sympos. Math., 29, Academic Press, New York, 1987; MR 89i:43007; T. Tahani, "Fonctions propres
de l'operateur de Laplace-Beltrami dans les boules hyperboliques reelle ou complex", Thesis, Univ. Nancy I, Vandoeuvre-les-Nancy, 1985; per bibl.; T.
Kawazoe and T. Tahani, Tokyo J. Math. 11 (1988), no. 1, 37--55; MR 89h:22016]. However, their arguments are slightly dependent on each circumstance
of the group. Therefore, it is worthwhile to give another proof which treats the problem uniformly, and apply it to the case of ${\rm Sp}(n,1)$. Now let $G$ be
one of the classical real rank one semisimple Lie groups: ${\rm SO}\sb 0(n,1)$, ${\rm SU}(n,1)$ and ${\rm Sp}(n,1)$. In $§4$ we prove that if a real-valued
$C\sp 2$ function $F$ on $G/K$ satisfies (1)--(3) and (4) $F$ is $M$-invariant, then $F$ is determined by the Poisson kernels. In $§5$ we try to remove this
additional condition. Although we can remove it in the cases ${\rm SO}\sb 0(n,1)$ and ${\rm SU}(n,1)$, we need an assumption for the case of ${\rm
Sp}(n,1)$, which can be stated as follows. We first identify $G/K$ $(G={\rm Sp}(n,1)$ and $K={\rm Sp}(n)\times{\rm Sp}(1))$ with the unit ball $D\sp n$ in
$\bold H\sp n$ where $\bold H$ is the quaternions, and denote the standard coordinates on $\bold H\sp n$ by $w\sb 1,w\sb 2,\cdots,w\sb n$. Since $F$ is
real analytic from (1), $F$ has a homogeneous expansion $F=\sum\sp \infty\sb {N=0}F\sb N$, where each $F\sb N$ is a homogeneous polynomial with
degree $N$. Then we easily see that there exists an element $k\sb 0$ in $K$ such that the rotation $F\sb {k\sb 0}$ of $F$ defined by $F\sb {k\sb
0}(w)=F(k\sb 0·w)$ $(w\in D\sp n)$ satisfies $(F\sb {k\sb 0})\sb 1(w)=(2n+1)(w\sb 1+\overline w\sb 1)$ (see (5.5)). Then the assumption which we need to
obtain the affirmative answer to the above problem is the following: (5) $F\sb {k\sb 0}(cw\sb 1,w\sb 2,\cdots,w\sb n)=F\sb {k\sb 0}(w\sb 1c,w\sb 2,\cdots,
w\sb n)$ for all $c$ in $\bold H$, i.e., $F\sb {k\sb 0}$ is a function of $w\sb 1+\overline w\sb 1$, $\vert w\sb 1\vert \sp 2$ and $w\sb s+\overline w\sb s$,
$w\sb si-i\overline w\sb s$, $w\sb sj-j\overline w\sb s$, $w\sb sk-k\overline w\sb s$ $(2\leq s\leq n)$. Then if $F$ satisfies (1)--(3) and (5), $F(gK)$ is
determined by the Poisson kernel $P(gK,k\sb 0M)$. Since $\bold R$ and $\bold C$ are abelian, the condition corresponding to (5) in the cases of $G={\rm
SO}\sb 0(n,1)$ and ${\rm SU}(n,1)$ holds automatically, and thus there is no need to assume (5)."

\vspace{.3in}

Kawazoe, Takeshi(J-KEIO); Tahani, Taoufiq(F-LILL) 
Correction to: "A characterization of the Poisson kernel associated with ${\rm SU}(1,n)$" [Tokyo J. Math. 11 (1988), no. 1, 37--55; MR 89h:22016].

Tokyo J. Math. 17 (1994), no. 2, 495--497.
22E30 (43A85)

Jacques Faraut:

In the paper cited in the heading the authors stated that a real
function on the Riemannian symmetric space $G/K$, $G={\rm SU}(1,n)$, 
which satisfies
$DF=0$, $DF^2=\lambda F^2$, $F(eK)=1$, where $D$ is the Laplace operator, is equal to the Poisson kernel $P(gK,kM)$ for some point $kM$ on the
boundary $K/M$. At some point of the proof there was a mistake in the computation of an integral. The idea of the new proof they propose is different, and
could be extended to the case of ${\rm Sp}(1,n)$. 

\vspace{.3in}

Kawazoe, Takeshi(J-KEIO) 
Atomic Hardy spaces on semisimple Lie groups. 
Japan. J. Math. (N.S.) 11 (1985), no. 2, 293--343.

The author gives a definition of Hardy spaces $H^1_{q,s}$ of $K$-invariant functions on a rank-one symmetric space $G/K$ of noncompact type. To some
extent he follows the lines of a paper by  R. R. Coifman and 
G. Weiss \ref[Bull. 
Amer. Math. Soc. 83 (1977), no. 4, 569--645;] to
define $(q,s)$-atoms as the building blocks of $H^1_{q,s}$, even though $G/K$ is not a space of homogeneous type. The fact that only atoms centered at
the origin are used makes these spaces too small to be considered analogues of the classical Hardy spaces. For instance, the definition proposed here,
when applied to the Euclidean symmetric space $ R^n\rtimes {\rm SO}(n)/{\rm SO}(n)$, does not lead to the space of radial functions in $H^1( R^n)$.
However, a characterization of $H^1 _{\infty,0}$ is given in terms of nondecreasing $L^1$ dominating functions and various results are given about the
boundedness from $H^1_{q,s}$ to $L^1$ of maximal operators, Fourier multipliers and pseudodifferential operators.


\vspace{.3in}
 Kawazoe, Takeshi Atomic Hardy spaces on semisimple Lie groups. Noncommutative harmonic analysis and Lie groups (Marseille-Luminy, 1985),
  189--197, Lecture Notes in Math., 1243, Springer, Berlin, 1987.
Kawazoe, Takeshi 
Atomic Hardy spaces on semisimple Lie groups. 
Noncommutative harmonic analysis and Lie groups (Marseille-Luminy, 1985), 189--197, 
Lecture Notes in Math., 1243, 
Springer, Berlin, 1987. 

Gerald B. Folland:

The author defines $H^1$ atoms and molecules in the context of $K$-bi-invariant functions on a semisimple Lie group. He shows that an appropriate grand
maximal function is bounded from atomic $H^1$ to $L^1$ and that molecules have atomic decompositions. 

{For the entire collection see MR 88b:22001.}

\vspace{.3in}

$KA$-wavelets on semisimple Lie groups and quasi-orthogonality of matrix coefficients. 
Infinite dimensional harmonic analysis (Kyoto, 1999), 238--252, 
Gräbner, Altendorf, 2000. 

This is an excellent article connecting integral wavelet transforms
and representations of semisimple Lie groups. 
Emphasis is placed on the group
$G:= {\rm SU}(1,1)$, the weighted Bergman spaces $\mathcal{H}_h$ and
the holomorphic discrete series of $G$. 
More precisely, the author proves that
there are a $\varphi\in\mathcal{H}:={\rm Cal}\,\mathcal{ H}_{1/2}$ and a
representation $T$ of $G$ over $\mathcal{ H}$ 
such that $$f=\text{const}·\int_K dk\int_A\langle
f, T(ka_t)\varphi\rangle T(ka_t)\varphi\sinh2t\,dt,$$ for all $f\in\mathcal{ H}$, a finite dimensional subspace, where $\langle,\rangle$ denotes the scalar product in
${\rm Cal}\,\mathcal{ H}$, and $K$ and $A$ denote the groups of Euclidean and hyperbolic rotations, respectively. 

The article will be useful for a graduate course in wavelet and group theory. 



Wavelet transforms associated to a principal series representation of semisimple Lie groups. I, II. 
Proc. Japan Acad. Ser. A Math. Sci. 71 (1995), no. 7, 154--157, 158--160.

 "We investigate a transform associated to a principal series representation of noncompact semisimple Lie groups and we obtain a
generalization of the Grossmann-Morlet transform and the Calderón identity. A transform associated to the analytic continuation of the holomorphic discrete
series and its limit will be treated in a forthcoming paper \ref[T. Kawazoe, "A transform associated to the analytic continuation of the holomorphic discrete
series of a semisimple Lie group", manuscript; per bibl.]. 

"Let $G$ be a noncompact connected semisimple Lie group with finite center and $P=MAN$ a parabolic subgroup of $G$. Let $\pi_\lambda={\rm
Ind}^G_P(1\otimes e^\lambda\otimes 1) (\lambda\in {a}^*_ C)$ denote a principal series representation of $G$ and $(\pi_\lambda,L^2(\overline{N},
e^{-2{\rm Im}\,\lambda(H(\overline n))}d\overline n))$ $(\overline N=\theta(N))$ the noncompact picture of $\pi_\lambda$. Let $\sigma_\omega$ denote an
irreducible unitary representation of $\overline N$ corresponding to $\omega\in\overline{ n}{}^*_ C$ and $(S,ds)$ a subset of $MA$ with measure $ds$.
In Part I we assume that there exists a $\phi\in\mathcal{ S}'(\overline N)$
satisfying the following admissible 
condition: for all $\omega\in V'_T$
$$\sigma_\omega(\phi)\sigma_\omega(\phi)^*=n_\phi(\omega)I,\qquad{\rm
i}$$ 

$$0<\int_S n_\phi({\rm Ad}(s)\omega)ds=c_{S,\phi}<\infty,\qquad{\rm
ii}$$ 
where $c_{S,\phi}$ is independent of $\omega$. Then for all such
$\phi$ we can deduce the inversion 
formula: $$f(x)=c^{-1}_{S,\phi}\iint_{\overline{N}\times
S}\langle
f,\pi_{-i\rho}(\overline{n}s)\phi\rangle\pi_{-i\rho}(\overline{n}s)\phi(x)d\overline{n}ds\ 
\forall f\in\mathcal{ S}(\overline N),$$ where $\langle·,·\rangle$ is the
inner product of $L^2(\overline N)$. A number of well-known examples of wavelet transforms arise from this scheme through the explicit form of $\phi$.
However, in the case of $G={\rm SL}(n+2,\bold R) (n\geq 1)$ and $\overline N\cong H_n$, the $(2n+1)$-dimensional Heisenberg group, the above formula
does not cover the three examples constructed by C. Kalisa and B. Torrésani \ref[see Ann. Inst. H. Poincaré Phys. Théor. 59 (1993), no. 2, 201--236; MR
95i:22033]. Therefore, in order to obtain a widespread application we need to generalize this formula."


Kawazoe, Takeshi(J-KEIOE) 
Wavelet transform associated to an induced representation of ${\rm SL}(n+2,\bold R)$. (English. English, French summary) 
Ann. Inst. H. Poincaré Phys. Théor. 65 (1996), no. 1, 1--13.
22E70 (43A80 81R30)

G. C. Bohnké:

Since the paper of A. Grossmann, J. Morlet and T. Paul \ref[J. Math. Phys. 26 (1985), no. 10, 2473--2479; MR 86k:22013] much work on the "continuous
wavelet transform" has been done, more or less in the spirit of Lie group theory. Here the author constructs the wavelet transform via the induced
representation machinery in the ${\rm SL}(n+2,\bold R)$ case. 

From the summary: "Let $G={\rm SL}(n+2,\bold R)$ and let $P=MAN$ be a parabolic subgroup of $G$ such that $N$ is isomorphic to the Heisenberg group
$H_n$. Let $1\otimes e^\lambda\otimes 1$ be a representation of $P$ and let $\pi_\lambda=\break {\rm Ind}_P^G(1\otimes e^\lambda\otimes 1)$ be the
induced representation of $G$ acting on $L^2(H_n)$. In this paper we
obtain a condition on $\lambda$ and
 $\psi\in \mathcal{ S}'(H_n)$ for which the matrix
coefficients $\langle f,\pi_\lambda(g)\psi\rangle_{L^2(H_n)}$ are square-integrable on a subgroup $\overline NA_1\simeq H_n\times \bold R$ of $G$ and
$\|f\|^2_{L^2(H_n)}=c\iint_{\overline NA_1}|\langle f,\pi_\lambda(\overline na_1)\psi\rangle_{L^2(H_n)}|^2d\overline nda_1\text{ for all } f\in \mathcal{ S}(H_n).$" 

Examples are given for several admissible functions $\psi (h)=\alpha(p,q)\beta(t)$, $h=(p,q,t)\in H_n\approx\bold R^n\times\bold R^n\times \bold R$. (In the
case of ${\rm SL}(2,\bold R)$, the function $\alpha(p,q)$ is disregarded and one recovers the classical wavelet transform associated to the affine "$ax+b$"
group.) 

The author also announces further results in a more general setting which will appear in forthcoming papers.


-------------------------------------------

Kenig, C. E.; Stanton, R. J.; Tomas, P. A. Divergence of eigenfunction expansions. J. Funct. Anal. 46 (1982), no. 1, 28--44.


The authors prove transplantation theorems for families of commuting differential operators on a smooth paracompact $n$-dimensional manifold $\Omega$. These allow us to deduce from uniform
boundedness as $R\rightarrow\infty$ of operators on $L^p(\Omega)$ of the form $Q_Km_R(P_1,\cdots,P_k)Q_K$, boundedness of the operator $m(p_1(x,\xi),\cdots,p_k(x,\xi))$ on $L^p(
R^n)$. (Here, $m\colon R^k\rightarrow R$ is a bounded Borel function, $\{P_1,\cdots,P_k\}$ a commuting set of symmetric differential operators with selfadjoint extensions to $L^2(\Omega)$,
$p_j$ is the principal symbol of $P_j$, $K$ a subset of $\Omega$ of positive measure, $x$ a point of density of $K$, and $Q_K\colon L^2\rightarrow L^2\colon f\rightarrow\chi_Kf$. If $m_j$ is
the degree of $P_j$, then $m_R(x_1,\cdots,x_k)$ is defined to be $m(R^{-m_1}x_1,\cdots,R^{-m_k}x_k)$.) The method of proof is based on a theorem of B. S. Mityagin [ Linear operators and
approximation, II\/ (Oberwolfach, 1974), pp. 521--530, Birkhäuser, Basel, 1974] combined with a theorem of Rellich's on the convergence of spectral expansions. These techniques
are also used to give weak type $(p,p)$ results. 

The transplantation theorems are then combined with results of Kenig and Tomas [Bull. Amer. Math. Soc. (N.S.) 1 (1979), no. 4, 694--697; MR 81g:42019] to give negative results on summability
methods for a noncompact semisimple Lie group $G$. For example, if $m$ is a bounded Borel function on $ R^l$, not identically zero, such that $m(x)=O(|x|^{-\varepsilon})$ for some
$\varepsilon>0$, and $S_R$ denotes the summability method on $G$ defined by $m$, then for each $p\neq 2$, there is $f\in L^p(G)$ so that $\|S_Rf-f\|_p\rightarrow 0$. If $1<p<2$, then for
some $f\in L^p(G)$, $\sup_R|S_Rf|=\infty$ almost everywhere. Another application: Projection onto the discrete series of $\text{SL}(2, R)$ is $L^p$ bounded if and only if $p=2$. (This answers a
question of Stein.)



----by A. H. Dooley 



-----------------------------------


Cowling, Michael 
The Kunze-Stein phenomenon. 
Ann. Math. (2) 107 (1978), no. 2, 209--234.

Let $G$ be a connected semisimple Lie group with finite center. In this interesting paper the author studies the convolution of functions on $G$. The
following theorem is proved: if $1\leq p<2$, then $L^p(G)*L^2(G)\subseteq L^2(G)$. Special cases of this result were obtained by several authors.

-------------------------------------

Kunze, R. A.; Stein, E. M. 
Uniformly bounded representations and harmonic analysis of the $2\times 2$ real unimodular group. 
Amer. J. Math. 82 1960 1--62.

This paper contains a remarkably detailed study of representations of and harmonic analysis on the group $G$ of $2\times 2$ real unimodular matrices. The
continuous irreducible unitary representations of $G$ were found long
ago by Gel'fand and Neumark 
[Acad. Sci. USSR J. Phys. 10 (1946),
93--94; MR 8, 132; Izv. Akad. Nauk SSSR Ser. Mat. 11 (1947), 411--504; MR 9, 495] and independently by V. Bargmann [Ann. of Math. (2) 48 (1947),
568--640; MR 9, 133]. Plancherel's formula for this group was established by Harish-Chandra [Proc. Nat. Acad. Sci. U.S.A. 38 (1952), 337--342; MR 13,
820]. To explain the results of this paper, some notation is needed. 
A generic element $g$ of $G$ is a matrix 
$\left( \begin{array}{cc}
 a & b \\ 
c & d 
\end{array} \right)$;
$ad-bc=1$; $a,b,c,d\in R$. For $g\in G$, $x\in R$, and $s\in C$, let $\phi^+(g,x,s)=|bx+d|^{2s-2}$, $\phi^-(g,x,s)=\text{sgn}(bx+d)\phi^+(g,x,s)$. For $g\in G$
and $x\in R$, let $g(x)=(ax+c)/(bx+d)$. For complex-valued functions $f$ on $ R$, let $$ (v^±(g,s)f)(x)=\phi^±(g,x,s)f\circ g(x). $$ The linear operators
$v^±(g,s)$ obviously provide representations of $G$. The representations $g\rightarrow v^±(g,\frac 1{2}+it) (t\in R)$ acting on $L_2( R)$ are continuous,
irreducible and unitary, and are called the two principal continuous series. The representations $g\rightarrow v^+(g,\sigma) (0<\sigma<{\textstyle\frac
1{2}})$, acting on the Hilbert space $H_\sigma$ of functions on $ R$ with inner product $$ a_\sigma\int_{ R}\int_{ R}f(x)\overline{f(y)}|x-y|^{-2\sigma}\,dxdy,
$$ are also continuous, irreducible and unitary, and are called the complementary series. Finally, there are two discrete series of continuous irreducible
unitary representations of $G$; these play only a minor rôle in the present paper. 

A main result of the paper is that the representations of the principal and complementary series can be analytically continued into the set $\{s\in C\colon
0<\text{Re}(s)<1\}= S$ in the following sense. There are a separable
Hilbert space $\mathcal{H}$ and
 representations $g\rightarrow U^±(g,s)$ of $G$ on $\mathcal{H}$
such that: (1) $g\rightarrow U^±(g,s)$ is a continuous representation of $G$ for each $s\in S$; (2) $g\rightarrow U^±(g,{\textstyle\frac 1{2}}+it) (t\in R)$ is
unitarily equivalent to the representation $g\rightarrow v^±(g,{\textstyle\frac 1{2}}+it)$ of the principal continuous series; (3) $g\rightarrow U^+(g,\sigma)
(0<\sigma<{\textstyle\frac 1{2}})$ is unitarily equivalent to the representation $g\rightarrow v^+(g,\sigma)$ of the complementary series; (4) for $g$ fixed in
$G$, and $\xi,\eta$ fixed in $\mathcal{ H}$, the function
$s\rightarrow\langle U^±(g,s)\xi,\eta\rangle$ is analytic 
in $S$; 
$$ \sup\{\|U^±(g,\sigma+it)\|\colon g\in
G\}\leq A_{\sigma,\varepsilon}(1+|t|)^{|\sigma-1/2|(1+\varepsilon)}
\qquad(5) $$ 
for $0<\sigma<1$ and $\varepsilon>0$, where $A_{\sigma,\varepsilon}>0$ and is
bounded on every interval $0<\alpha\leq\sigma\leq\beta<1$. 

The authors use the representations $U^±(g,s) (s\in S)$ to obtain a complete analogue of the Hausdorff-Young theorem for $G$. A bounded linear operator
$A$ on the separable Hilbert space $\mathcal{ H}$ is in $\mathcal{ B}_p (1\leq p<\infty)$ if the non-negative operator $(A^*A)^{1/2}=|A|$ has discrete spectrum
$(\lambda_1,\lambda_2,\cdots,\lambda_n,\cdots)$ and
$\|A\|_p=[\sum_{n=1}^\infty\lambda_n{}^p]^{1/p}$ is finite. 
For $f\in L_1(G)$ and $s\in S$, let
$\mathcal{F}^±(s)=\int_GU^±(g,s)f(g)\,dg$. 
This is the [operator-valued] Fourier transform of $f$. Let $1<p<2$,
and $q=p/(p-1)$. 
There is a measure $\mu_{q,\sigma}$ on
$ R$ such that for all $f\in L_1(G)\cap L_p(G)$, $$
\left[\int_{-\infty}^\infty\|\mathcal{F}^±(\sigma+it)\|_q{}^q\,d\mu_{q,\sigma}(t)\right]^{1/q}\leq\|f\|_p.
\qquad (1) $$ The
Fourier transform admits a [unique] linear bounded extension over all
of $L_p(G)$ for which (1) holds. 
Furthermore, $\mathcal{ F}^±(s)$ is analytic in $s$.
Analogous results using only the discrete series hold for $p\in[1,2]$. 

The Hausdorff-Young inequality (1), involving the whole strip $ S$ instead of only the line $\text{Re}\,s={\textstyle\frac 1{2}}$, has some curious
consequences. If $f\in L_2(G)$ and $g\in L_p(G)$, $1\leq p<2$, then $f*g\in L_2(G)$ and $\|f*g\|_2\leq A_p\|f\|_2·\|g\|_p$. If $g\in L_2(G)$, then $f*g\in L_q(G)$
for all $q\in\,]2,\infty]$, and $\|f*g\|_q\leq A_q\|f\|_2·\|g\|_2$. Both of these assertions hold trivially for compact groups and fail for the simplest non-compact
Abelian groups, e.g., for the group $ R$. 

This paper is nearly self-contained, and it is very carefully written. It is an important step in realizing the possibilities for detailed harmonic analysis that are
implicit in the Gel'fand-Raikov theorem.


------------------------------------------

Koornwinder, Tom H.(NL-VUAM) 
Jacobi functions and analysis on noncompact semisimple Lie groups. 
Special functions: group theoretical aspects and applications, 1--85, 
Math. Appl., 
Reidel, Dordrecht, 1984. 

From the introduction: "There are many group-theoretic interpretations of Jacobi functions, first as spherical functions on noncompact Riemannian
symmetric spaces of rank one, but also as associated spherical functions, intertwining functions, matrix elements of (representations of) ${\rm SL}(2, R)$ and
spherical functions on certain nonsymmetric Gel'fand pairs. This makes Jacobi functions an ideal subject for the case study of the interactions
between special functions and group theory." 

This paper is a nice survey of this topic, with the personal point of view of the author, and with many published and unpublished results of his own. At the
same time the author has gathered together a great amount of information about the numerous ramifications of the subject. After recalling classical facts first
about the Jacobi functions and the Jacobi transform, then about the
theory of Gel'fand pairs and spherical 
functions, the author studies the Jacobi
functions as spherical functions on rank one symmetric spaces, as associated spherical functions and as functions on certain non-Riemannian symmetric
spaces. He studies further the Abel transform using the Riemann-Liouville and Weyl transforms, and using them, he gives a proof of the Paley-Wiener
theorem for the Jacobi transform. The last parts are devoted to the convolution structure associated with the Jacobi transform, the addition formula and the
dual convolution structure. 

{For the entire collection see MR 85i:22003.}

                                 Reviewed by Jacques Faraut 

-----------------------------------------------------------------

Flensted-Jensen, Mogens; Koornwinder, Tom 
The convolution structure for Jacobi function expansions. 
Ark. Mat. 11, 245--262. (1973). 

G. Gasper:

Let $R_µ{}^{(\alpha,\beta)}(x)=F[-µ,µ+\alpha+\beta+1;\alpha+1;(1-x)/2]$, where $F$ is the hypergeometric function. The Jacobi functions (a noncompact
analogue of the Jacobi polynomials $R_n{}^{(\alpha,\beta)}(x)$, $n=0,1,2,\cdots$) are defined by
$\phi_\lambda{}^{(\alpha,\beta)}(t)=R_{(i\lambda-\rho)/2}^{(\alpha,\beta)}(\cosh 2t)$, where $\rho=\alpha+\beta+1$, $0\leq t<\infty$, and $\lambda$ is a
complex number. H. Bateman's formula [ Partial differential equations of mathematical physics, Cambridge Univ. Press, Cambridge, 1932; Zbl 4, 214; revised edition,
Dover, New York, 1944; MR 6, 86; reprint of first edition, Cambridge Univ. Press, New York, 1959] for the product of two Jacobi polynomials,
$R_n{}^{(\alpha,\beta)}(x)R_n{}^{(\alpha,\beta)}(y)=\sum_ka_k(x+y)^kR_k{}^{(\alpha,\beta)}((1+xy)/(x+y))$, is extended to the case in which $n$ is not
necessarily an integer, and the extension is used to show that if $\alpha\geq\beta\geq-1/2$, then the product
$\phi_\lambda{}^{(\alpha,\beta)}(t_1)\phi_\lambda{}^{(\alpha,\beta)}(t_2)$ of two Jacobi functions can be represented as an integral of a Jacobi function
$\phi_\lambda{}^{(\alpha,\beta)}(t_3)$ with a nonnegative kernel. The integral is then used to define a generalized translation operator, the convolution
product of two suitable functions, and to obtain convolution structure results for $\alpha\geq\beta\geq-1/2$ similar to those which were obtained by the
reviewer [Ann. of Math. (2) 95 (1972), 261--280] for
Jacobi series with less restrictive conditions 
on $(\alpha,\beta)$.

                                 ( Reviewed by G. Gasper )
--------------------------------------

Koornwinder, Tom H.(NL-AMSTM) 
Fast wavelet transforms and Calderón-Zygmund operators. (English. English summary) 
Wavelets: an elementary treatment of theory and applications, 161--182, 
Ser. Approx. Decompos., 1, 
World Sci. Publishing, River Edge, NJ, 1993. 

The paper is a detailed account of a part of a previous paper \ref[G. Beylkin, R. R. Coifman and V. V. Rokhlin, Comm. Pure Appl. Math. 44 (1991), no. 2,
141--183; MR 92c:65061] connected with utilization of wavelet techniques for computation, with prescribed accuracy, of the action of a
Calderón-Zygmund operator on a function on $[0,1]$. 

{For the entire collection see MR 94c:42001.}


---------------------------------------------------

Kawazoe, Takeshi(J-KEIOF); Liu, Jianming(PRC-BJ) 
On a weak $L\sp 1$ property of maximal operators on non-compact semisimple Lie groups. (English. English
summary) 
Tokyo J. Math. 25 (2002), no. 1, 165--180.

Let $G$ be a non-compact connected simple Lie group with finite center, and a maximal compact subgroup $K$. For
$r>0$ let $B(r)\subseteq G$ denote the set of all $g\in G$ such that the Riemannian distance from $gK$ to $K$ in $G/K$ is
less than $r$. For a $K$-bi-invariant absolutely integrable function $f\colon G\to \Bbb C$, let $$M_{\rm
HL}f(g)=\underset{r>0}\to{\sup}\int_{B(r)}|f(gh)|\,dh \qquad (g\in G).$$ This is the Hardy-Littlewood maximal operator on
$G$. The main result of the paper (Theorem 4.1) states that for $G$ other than ${\rm SL}(n,\Bbb R), (n=3,4)$, or $\rm
SO(3,2)$, the operator $M_{\rm HL}$ satisfies a weak type $L^1$-inequality and is of strong $(L^p,L^p)$-type for
$1<p\leq \infty$.

                       Reviewed by Tomasz Przebinda 

--------------------------------------------------

Liu, Jian Ming(PRC-BJ-SM); Peng, Li Zhong(PRC-BJ-SM) 
Weighted Plancherel formula on bounded symmetric domains. (Chinese. English, Chinese summary) 
Acta Math. Sinica 45 (2002), no. 2, 215--220.
32A50 (32M15 43A90)

Consider a Hermitian symmetric space $D=G/K$ and a one-dimensional unitary representation $\tau$ of $K$. The space
of $L^2$-functions $f(g)$ on $G$ that transform on the right under $K$ according to $\tau$, namely $f(gk)=\tau(k)f(g)$,
forms a unitary representation of $G$ and its irreducible decomposition has been given by N. Shimeno \ref[J. Funct. Anal.
121 (1994), no. 2, 330--388; MR 95b:22036]. In the present paper the authors consider the bounded realization of $D$
and identify the above $L^2$ space as the space of $L^2$-functions on $D$ with a weighted measure. They then derive
the corresponding weighted Plancherel formula from that of Shimeno.

                        Reviewed by Genkai Zhang 

--------------------------------------------------------------------

Liu, Jianming(PRC-BJ-SM) 
The Fourier transform for homogeneous vector bundles over quaternion unit disk. (English. English summary) 
Chinese Ann. Math. Ser. B 21 (2000), no. 3, 343--350.

The quaternion unit disk is a Riemannian symmetric space of rank one. As a homogeneous space it is $G/K$ with $G={\rm
Sp}(1,1)$ and $K={\rm Sp}(1)\times{\rm Sp}(1)$. The homogeneous vector bundles considered are given by irreducible
representations of $K$ which are trivial on one of the ${\rm Sp}(1)$ factors. For the space of square-integrable sections
of such a bundle the natural Fourier transform is considered; the inversion formula and the Plancherel formula are
proved. The case of general sections is reduced to that of "spherical" sections; for these the inversion formula is
obtained from the inversion formula of the Jacobi transform.

                         Reviewed by A. Korányi 
--------------------------------------------------------

Liu, Jianming(PRC-BJ) 
Maximal functions associated with the Jacobi transform. (English. English summary) 
Bull. London Math. Soc. 32 (2000), no. 5, 582--588.

The paper defines a Hardy-Littlewood maximal operator associated with the Jacobi transform and shows that this
operator is weak-type $(1,1)$ and strong type $(p, p)$, $p>1$. 

Consider the Jacobi function $\phi_\lambda(t)$ of order $(\alpha,\beta)$ $(\alpha\neq-1,-2,\cdots)$; the Jacobi transform
is defined by $${\widehat f(\lambda)=\int_0^\infty f(t)\phi_\lambda(t) \Delta(t)dt},$$ where $\Delta(t)=(2\sinh t)^{2\alpha+1}
(2\cosh t)^{2\beta+1}$. There is a convolution product associated to the Jacobi transform which has the property that
$\widehat{f*g}(\lambda)=\widehat f (\lambda) \,\widehat g( \lambda)$. Set $\chi_r=(1/|[0,r]|)\chi_{[-r,r]}$, where for any set
$A, |A|=\int_A \Delta(t)dt$. With this, a Hardy-Littlewood maximal operator can be defined as
$Mf(t)=\sup_{r>0}\chi_r*|f|(t)$. 

The weak-type $(1,1)$ estimate $$|\{Mf>\lambda\}|\leq(C/\lambda)\int_0^\infty |f(t)|\Delta(t)dt$$ is shown using a covering
lemma adapted to the measure $|·|$ and by making estimates on the kernel $\chi_r$ and its translations. That $M$ is
bounded on $L^\infty$ is straightforward; the $L^p$ estimates follow by interpolation.

                        Reviewed by Charles N. Moore 

--------------------------------------------------------

Liu, Jianming(PRC-BJ); Zheng, Weixing(PRC-NAN) 
A Hardy-Littlewood theorem for weighted spaces. (English. English summary) 
Acta Math. Sci. (English Ed.) 17 (1997), no. 2, 211--218.

The authors prove theorems for Fourier-Jacobi (F-J) transforms and for Fourier-Bessel (F-B) transforms which are
related to weighted inequalities of Hardy-Littlewood type for standard Fourier transforms. 

For F-J transforms, let $\alpha\geq\beta\geq-{1\over2}$ and $\alpha\not=-{1\over2}, \Delta(t)=$\break $(2·\sinh
\,t)^{2\alpha+1}(2·\cosh\,t)^{2\beta+1}, t>0$, and $\rho=\alpha+\beta+1$. Consider the Jacobi functions
$$\phi_\lambda(t)=F\bigg({\rho-i\lambda\over2} ,{\rho+i\lambda\over2};\alpha+1;-{\rm sinh}^2t\bigg),\quad
dµ(t)=\Delta(t)dt.$$ The F-J transform is defined by $\hat f(\lambda)=\int^\infty_0f(t)\phi_\lambda(t)dµ(t)$. Let
$$c(\lambda)={2^{\rho-i\lambda}\Gamma(\alpha+1) \Gamma(i\lambda)\over\Gamma({1\over2}(i\lambda+\rho))
\Gamma({1\over2}(i\lambda+\alpha-\beta+1))}.$$ Theorem 1. Suppose $2\leq q<\infty$, then the F-J transform can be
defined for $f$ such that $f(t)(t\Delta(t))^{1-2/q}\in L( R^+,dµ(t))$,
and there exists 
a constant $A_q$ independent of $f$
such that 
\begin{align*}
\Big(\int^\infty_0|\hat{f}(\lambda)|^q|c(\lambda)|^{-2}d\lambda\Big)^{1/q}\leq\\
A_q\Big(\int^\infty_0|f(t)|^q(t\Delta(t))^{q-2}dµ(t)\Big) ^{1/q}. 
\end{align*}

For F-B transforms, let $\alpha>-{1\over2},\ \psi_\lambda(t)=a(\alpha)(\lambda t)^{-\alpha}J_\alpha(\lambda t),\ t>0,
a(\alpha)=2^\alpha\Gamma(\alpha+1)$, and $J_\alpha$ denote the Bessel function of order $\alpha$. The F-B transform
is defined by $\tilde f(\lambda)=\int^\infty_0f(t)\psi_\lambda(t)d\nu(t)$. The authors also prove Theorem 2. Suppose $2\leq
q<\infty$; then the F-B transform can be defined for $f$ such that $f(t)(t^{2\alpha+2})^{1-2/q}\in L( R^+,d\nu)$, and there
exists $A_q$, such that $$\Big(\int^\infty_0|\tilde f(\lambda)|^qd\nu(\lambda)\Big)^{1/q}\leq
A_q\Big(\int^\infty_0|f(t)|^qt^{(2\alpha+2)(q-2)}d\nu(t)\Big)^{1/q}.$$

                        Reviewed by Gary Sampson 

------------------------------------------------------

Liu, Jianming(PRC-NAN); Zheng, Weixing(PRC-NAN) 
Weighted Plancherel formula on unit ball in $ R\sp n$. (English. English summary) 
Sci. China Ser. A 39 (1996), no. 9, 935--944.

The weighted Plancherel formula on the unit ball of ${\bold C}^n$ has been studied in several recent papers. In this
paper the authors study the weighted Plancherel formula for the unit ball $B$ of ${\bold R}^n$. More precisely, they
determine the decomposition of the action of the group $G={\rm SO}_0(1,n)$ on the space $L^2(B,dµ_{\nu})$, where
$dµ_{\nu}(x)=\break (1-|x|^2)^{(\nu -n-1)/2}dm(x)$, and $dm$ is the Lebesgue measure. The group $G$ acts on $B$ and
the $G$-action on $L^2(B,dµ_{\nu})$ is given by $T_g^{\nu}f(x)=f(g·x)\bigl(\det g'(x)\bigr)^{\nu/2(n+1)}$. The authors use
the same method as in the case of the ball of ${\bold C}^n$, i.e. the spectral decomposition of the invariant Laplacian
corresponding to the representation $T^{\nu}$. 

It was not noticed that the result follows directly from the classical Planche\-rel formula for the Riemannian symmetric
space $G/K={\rm SO}_0(1,n)/{\rm SO}(n)$. In fact, the representation $T^0$ is the left regular representation of $G$ on
$L^2(G/K)$, and the representation $T^{\nu }$ is equivalent to $T^0$. The map $$f(x)\mapsto (1-|x|^2)^{\nu/2}f(x),\quad
L^2(B,dµ_{\nu})\rightarrow L^2(B,dµ_0),$$ intertwines the representations $T^{\nu}$ and $T^0$. It follows easily from the
relation $$\det g'(x)=\Bigl({1-|g·x|^2\over 1-|x|^2}\Bigr)^{(n+1)/2}.$$ 

The case of the unit ball of ${\bold C}^n$ is different because in this case the group $G={\rm SU}(1,n)$ acts by
holomorphic transformations, and the representation $T^{\nu}$ involves an automorphy factor which is a power of the
complex Jacobian.

                        Reviewed by Jacques Faraut 
--------------------------------------------------------------

Liu, Jianming(PRC-NAN); Zheng, Weixing(PRC-NAN) 
Complex-weighted Plancherel formula and Jacobi transform. 
Chinese Sci. Bull. 41 (1996), no. 6, 454--458.

The authors consider an invariant Laplacian operator induced from the projective representation with a complex power
for a Möbius group on the unit disc in the complex plane and the eigenfunctions for the operator. Then, they examine the
spherical integral transform by the eigenfunctions. By using the Jacobi transform, they establish the Paley-Wiener type
theorem, inversion formula and Plancherel formula for this spherical transform as the generalizations of the related results
of S. Helgason, J. Peetre and H. Liu. 

They extend the results for real parameters to those for complex parameters in the problem, but it seems that the
motivation of this research is not shown clearly.

                        Reviewed by Saburou Saitoh 

-------------------------------------------------------

Liu, Jianming(PRC-NAN); Zheng, Weixing(PRC-NAN) 
The decomposition of the representations $T\sp v$ and the Plancherel formula for the universal covering group of
${\rm SU}(1,1)$. (English. English summary) 
Approx. Theory Appl. (N.S.) 11 (1995), no. 3, 52--61.

Let $G$ be ${\rm SU}(1,1)$ and $K$ the maximal compact subgroup of $G$. The authors consider $L^2$-sections of some
line bundle over $G/K$ as a unitary representation $T^v$ of $\tilde G$. Here $\tilde G$ is the universal covering group of
$G$. The decomposition of $T^v$ into irreducible unitary representations is obtained.

                        Reviewed by Jing-Song Huang 

-----------------------------------------------------

\vspace{0.46in}


--------------------------------------------------------------------

\begin{thebibliography}{99}
%\input{ref.tex}
\bibitem{Ank} J.-Ph. Anker , Sharp estimates for some functions of the Laplacian on
   noncompact symmetric spaces. Duke Math. J. 65 (1992), pp. 257-297.

\bibitem{AsKooSch}
  Special functions: group theoretical aspects and
applications. Edited by R. A. Askey, T. H. Koornwinder 
and W. Schempp. {\em Mathematics
  and its Applications}. D. Reidel Publishing Co., Dordrecht, 1984. 

\bibitem{Cl}
Clerc, Jean-Louis Bochner-Riesz means of $H\sp p$ functions $(0<p<1)$ on compact Lie groups. Noncommutative harmonic analysis and Lie groups (Marseille-Luminy, 1985),
  86--107, Lecture Notes in Math., 1243, Springer, Berlin,
1987. (Reviewer: Fulvio Ricci) 

\bibitem{ClSte}
J. L. Clerc and E. M. Stein , Lp-multipliers for non-compact symmetric spaces.
   Proc. Nat. Acad. Sci. USA 71 (1974), pp. 3911-3912.

\bibitem{Cow}
 Cowling, Michael G. Harmonic analysis on semigroups, {\em Ann. of
Math.(2)}, {\bf 117}, (1983), 
no. 2, 267--283.

\bibitem{Cow}
 Cowling, Michael, The Kunze-Stein phenomenon, {\em Ann. Math.(2)},
{\bf 107}(2), (1978), 209--234. 
 
\bibitem{CowGM}
 Cowling, Michael; Giulini, S.; Meda, Stefano Oscillatory multipliers
related to the wave equation on noncompact 
symmetric spaces, {\em  J.
  London Math. Soc}., (2) 66 (2002), no. 3, 691--709.

\bibitem{CowGM}
Cowling, Michael; Giulini, Saverio; Meda, Stefano,
 $L\sp p$-$L\sp q$ estimates for functions of the Laplace-Beltrami operator on
  noncompact symmetric spaces. I. Duke Math. J. 72 (1993), no. 1,
 109--150. 

\bibitem{CowGM}
Cowling, Michael; Giulini, Saverio; Meda, Stefano $L\sp p$-$L\sp q$-estimates for functions of the Laplace-Beltrami operator on
  noncompact symmetric spaces. II. J. Lie Theory 5 (1995), no. 1, 1--14.

\bibitem{CowGM}
Cowling, M.; Giulini, S.; Meda, S. $L\sp p$--$L\sp q$ estimates for functions of the Laplace-Beltrami operator on noncompact symmetric
  spaces. III. Ann. Inst. Fourier (Grenoble) 51 (2001), no. 4,
1047--1069. 

\bibitem{CowSik}
 Cowling, Michael, Sikora, Adam, A spectral multiplier theorem for a
sublaplacian on $\rm SU(2)$,
{\em  Math. Z}., {\bf 238}(1), (2001), 1--36.

\bibitem{DeMMau}
De Michele, Leonede; Mauceri, Giancarlo $H\sp p$ multipliers on
stratified groups, {\em Ann. Mat. Pura Appl}., {\bf 148}(4), (1987),
353--366. 
(Reviewer: Gerald B. Folland)

\bibitem{Fl-J} M. Flensted-Jensen , Paley-Wiener type theorems for a differential operator
   connected with symmetric spaces. Ark. Mat. 10 (1972), pp. 143-162. MathSciNet

\bibitem{FlKoo}
 Flensted-Jensen, Mogens; Koornwinder, Tom, The convolution structure
for Jacobi function expansions,
{\em Ark. Mat}., {\bf 11}, 245--262. (1973).

\bibitem{Fol}
Folland, Gerald B., {\em Harmonic analysis in phase space}, {\em Annals of
Mathematics Studies}, {\bf 122}. 
Princeton University Press, Princeton, NJ, 1989.

\bibitem{FoSte}
 G. B. Folland and E. M. Stein, {\em Hardy Spaces on Homogeneous
Groups}, {\bf Math.Notes}, {\bf 28}, Princeton Univ. Press, Princeton (1982).

\bibitem{GiuM}
Giulini, Saverio; Mauceri, Giancarlo Almost everywhere convergence of Riesz means on certain noncompact symmetric spaces. Ann. Mat. Pura Appl. (4) 159 (1991), 357--369.
  (Reviewer: Michael Cowling)

\bibitem{GiuMM}
Giulini, Saverio; Mauceri, Giancarlo; Meda, Stefano $L\sp p$ multipliers on noncompact symmetric spaces. J. Reine Angew. Math. 482 (1997), 151--175. (Reviewer: Tomasz
  Przebinda)

\bibitem{GiuSj}
Giulini, Saverio(I-GENOE); Sjögren, Peter, 
A note on maximal functions on a solvable Lie group. 
{\em Arch. Math. (Basel)}, {\bf 55}(2), (1990), 156--160.

\bibitem{Hel}
S. Helgason, {\em Differential Geometry and Symmetric Spaces}, Academic Press,
   San Diego (1962).

\bibitem{HulJen}
Hulanicki, Andrzej; Jenkins, Joe W. Almost everywhere summability on nilmanifolds. Trans. Amer. Math. Soc. 278 (1983), no. 2, 703--715. (Reviewer: J. Boidol) 

\bibitem{HulJen2}
Hulanicki, Andrzej; Jenkins, Joe W. Nilpotent Lie groups and summability of eigenfunction expansions of Schrödinger operators. Studia Math. 80 (1984), no. 3, 235--244.
  (Reviewer: L. Corwin) 22E30 (22E25 47B38)

\bibitem{HulJen3}
 Hulanicki, Andrzej; Jenkins, Joe W. Nilpotent Lie groups and eigenfunction expansions of Schrödinger operators. II. Studia Math. 87 (1987), no. 3, 239--252. (Reviewer: L.
  Corwin)

\bibitem{Ion}
Alexandru D. Ionescu, Fourier integral operators on noncompact symmetric spaces of real rank one. Journal of
Functional Analysis 174, 274--300 (2000).

\bibitem{Ion}
 Alexandru D. Ionescu, An endpoint estimate for the Kunze-Stein phenomenon and related maximal operators.
Annals of Mathematics 152, 259--275 (2000). 

\bibitem{Ion}
 Alexandru D. Ionescu, A maximal operator and a covering lemma on non-compact symmetric spaces.
Mathematical Research Letters 7, 83--93 (2000). 

\bibitem{Ion}
 Alexandru D. Ionescu, On the Poisson transform on symmetric spaces of real rank one. Journal of Functional
Analysis 174, 513--523 (2000). 

\bibitem{Ion}
 Alexandru D. Ionescu, Singular integrals on symmetric spaces of real rank one. To appear in Duke Mathematical
Journal.

\bibitem{Ion}
 Alexandru D. Ionescu, Singular integrals on symmetric spaces, II. Preprint 2001.

%\bibitem{Ion}
% Alexandru D. Ionescu, Rearrangement inequalities on semisimple Lie groups. Preprint 2001. 

\bibitem{Ion}
 Alexandru D. Ionescu and David Jerison, On the absence of positive eigenvalues of Schrodinger operators with rough
potentials. Preprint 2002.

\bibitem{Ka} Kawazoe, T., Hardy spaces and maximal operators on real
rank one semisimple Lie groups, {\em I}, {\em  Tohoku Math. J.(2)},
{\bf 52}(1), (2000), 1--18. (Reviewer: Gerald B. Folland)

\bibitem{Ka} Kawazoe, T.,  $L^1$ estimates for maximal functions and
Riesz transform on real rank $1$ semisimple Lie groups. {\em
J. Funct. Anal.}, {\bf 157}(2),
  (1998), 327--357.

\bibitem{Ka} Kawazoe, T., A characterization of the Poisson kernel on
the classical real rank one symmetric spaces, {\em Tokyo J. Math.},
{\bf 15}(2), (1992), 365--379.

\bibitem{Ka}
Kawazoe, T., Atomic Hardy spaces on semisimple Lie groups, {\em
Japan. J. Math. (N.S.)}, {\bf 11}(2), (1985), 293--343. (Reviewer: Fulvio
  Ricci)

\bibitem{Ka}
Kawazoe, T., Atomic Hardy spaces on semisimple Lie groups, {\em
Noncommutative harmonic analysis and Lie groups}
 (Marseille-Luminy, 1985),
  189--197, {\em Lecture Notes in Math.}, {\bf 1243}, Springer, Berlin, 1987. (Reviewer: Gerald B. Folland)

\bibitem{Ka}
Kawazoe, T., Wavelet transform associated to an induced representation
of ${\rm SL}(n+2,\bold R)$,
{\em Ann. Inst. H. Poincaré Phys. Théor.}, {\bf 65}(1),
  (1996), 1--13. (Reviewer: G. C. Bohnké) 
 
\bibitem{Ka}
Kawazoe, T., Wavelet transforms associated to a principal series
representation of semisimple Lie groups. I, II. 
{\em Proc. Japan Acad. Ser. A
  Math. Sci.}, {\bf 71(7)}, (1995), 154--157, 158--160.

\bibitem{Ka}
Kawazoe, T., $KA$-wavelets on semisimple Lie groups and
quasi-orthogonality of matrix coefficients. 
{\em Infinite dimensional harmonic
  analysis} (Kyoto, 1999), 238--252, Gräbner, Altendorf, 2000. 
                                
\bibitem{KaLiu} Kawazoe, T.; Liu, J. On a weak $L^1 1$ property of
maximal operators on non-compact semisimple Lie groups. {\em Tokyo
J. Math.}, {\bf 25}(1), (2002), 165--180.

\bibitem{KaTa}
Kawazoe, T., Tahani, Taoufiq, A characterization of the Poisson kernel
associated with ${\rm SU}(1,n)$, 
{\em Tokyo J. Math.}, {\bf 11}(1), (1988), 37--55. (Reviewer: Jacques
Faraut)

\bibitem{KaTa} Kawazoe, T., Tahani, Taoufiq, Correction to: "A
characterization of the Poisson kernel associated 
with ${\rm SU}(1,n)$" [Tokyo J.
  Math. 11 (1988), no. 1, 37--55; MR 89h:22016], {\em Tokyo J. Math.},
{\bf 17}(2), (1994), 495--497. (Reviewer: Jacques Faraut)
 
\bibitem{KST}
Kenig, C. E.; Stanton, R. J.; Tomas, P. A. Divergence of eigenfunction expansions. J. Funct. Anal. 46 (1982), no. 1, 28--44.
 
\bibitem{Koo}
 Koornwinder, Tom H. Jacobi functions and analysis on noncompact
semisimple Lie groups. 
Special functions: group theoretical aspects and
  applications, 1--85, Math. Appl., Reidel, Dordrecht, 1984. (Reviewer: Jacques Faraut)
 
\bibitem{Koo}
 Koornwinder, Tom H. Fast wavelet transforms and Calderón-Zygmund
operators.
 Wavelets: an elementary treatment of theory and applications,
  161--182, Ser. Approx. Decompos., 1, World Sci. Publishing, River
Edge, NJ, 1993. 

\bibitem{L}                               
 Liu, Heping The $H\sp p$ boundedness of Riesz means on the Heisenberg group. A Chinese summary appears in Acta Math. Sinica 39 (1996), no. 1, 140. Acta Math. Sinica
  (N.S.) 11 (1995), Special Issue, 18--25. (Reviewer: Norman J. Weiss)

\bibitem{LLu}
 Liu, He Ping; Lu, Shan Zhen The $H\sp p$-boundedness of the Riesz means for the eigenfunction expansions for elliptic operators with constant coefficients. Proc. Amer. Math.
  Soc. 122 (1994), no. 2, 487--494. (Reviewer: Günter Berger) 

\bibitem{Liu} Liu, Jianming,
 Maximal functions associated with the Jacobi transform, {\em
Bull. London Math. Soc}., {\bf 32}(5), (2000), 582--588.

\bibitem{Lo}
 N. Lohoué , Transformés de Riesz et fonctions sommables, {\em
Amer. J. Math}., {\bf 114}, (1992), pp. 875-9.
                                
%\bibitem{Perez}
%P\'erez, Carlos, Endpoint estimates for commutators of singular integral
%operators, {\em J. Funct. Anal}. {\bf 128} (1995), no. 1, 163--185. 


%\bibitem{Perez2}
%P\'erez, C. On a theorem of Muckenhoupt and Wheeden and a weighted
%inequality related to Schr\"odinger operators, {\em
%Trans. Amer. Math. Soc.}, {\bf 340} (1993), no. 2, 549--562.

\bibitem{ST}
 Stanton, Robert J.; Tomas, Peter A. Expansions for spherical functions on noncompact symmetric spaces. Acta Math. 140 (1978), no. 3-4, 251--276. 

\bibitem{ST2}
Stanton, Robert J.; Tomas, Peter A. 
Pointwise inversion of the spherical transform on $L\sp{p}(G/K)$, $1\leq p<2$. 
{\em Proc. Amer. Math. Soc.}, {\bf 73}(3), (1979), 398--404.

\bibitem{Ste}
 E. M. Stein, {\em Harmonic Analysis: Real-Variable Methods, Orthogonality, and
   Oscillatory Integrals}, Princeton Math. Ser. 43, Princeton Univ. Press, Princeton
   (1993).

\bibitem{St}



\bibitem{Stro}
 J. Strömberg , Weak type estimates for maximal functions on non-compact
   symmetric spaces, {\em Ann. of Math}., {\bf 114}, (1981), pp. 115-126.

\bibitem{TW}
 M. H. Taibleson and G. Weiss , The molecule characterization of certain
   Hardy spaces, {\em Astérisque}, {\bf 77}, (1980), pp. 68-149.

\bibitem{Wa}
 G. Warner Harmonic Analysis on Semi-Simple Lie Groups II,
   Springer-Verlag, Berlin/ New York (1972). 

\end{thebibliography}

\end{document} 












 













