\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,latexsym}
\topmargin=-0.703in
\textheight=9.2in
\oddsidemargin=0in
\textwidth=6.75in   
\pagestyle{empty}

\newcommand{\nd}{\noindent}

\begin{document}

\large 
\begin{center}
{\bf Math 141 ~Calculus I %~~~ (Sections 3--4)
 ~~~ Spring 2007}
\end{center}

%\normalsize 

\bigskip
\noindent
{\bf Instructor:} Dr.~Shijun Zheng\\

%\bigskip
%\noindent
%\begin{tabular}{ll}

\noindent
{Office: {LeConte 426} and Sumwalt 206J\\

\nd
{Office Hours:}  {WF 2:00--3:30pm or by appointment}\\

\nd
{Phone:}  {576-6350},  576-5985\quad  
{Email:}  {shijun@math.sc.edu }\\

%\end{tabular}

\nd
{\bf Lectures:} ~MWF 10:10am--11:00am, PSC 006\\
%\noindent
%\begin{tabular}{ll}
%{\bf Recitation:} & M 10:10--11:00 am in LC 112 for Section 7 and 
%M 11:15am--12:05pm in LC 115 for Section 8.\\
%{\bf Lab:} &W 10:10--11:00am in LC 102 for Section 7 and W 11:15am--12:05pm
%in LC 102 for Section 8.
%\end{tabular}

%\bigskip
\noindent
{\bf Teaching Assistant:} Theresa Sparacio\\

\nd
{\bf Course website}: http://www.math.sc.edu/{\verb+~+}shijun/teach2/141.html 

%\noindent
%\begin{tabular}{ll}
%{Office:}&{LeConte 300K}\\
%{Phone:} &{777-4319}\\
%{Email:} &{sparacio@mailbox.sc.edu}\\
%{Office Hours:} &{MW 12:10--1:10pm or by appointment}
%\end{tabular}

\bigskip
\noindent
{\bf Textbook:} Anton, Bivens, and Davis {\em Calculus} ~8th ed.

%\noindent
%{\bf Prerequisite:} A grade of C or better in Math 141.

\bigskip
\noindent
{\bf Grades:}  %Your grade in this course will be based on your performance 
%on quizzes, major tests, a final exam, and computer labs. The weights 
%assigned to each of these components will be:
  The weighting in your course score points (600 total) will be\\
\hspace*{.29635in} \qquad 200   Final Exam  \\
\hspace*{.29635in} \qquad100 each   Two midterm exams\\
\hspace*{.29635in} \qquad 100   Quizzes\\
\hspace*{.29635in} \qquad100   Maple projects\\
%\bigskip
%\begin{tabular}{rl}
%{75} & {labs}\\
%{35} & {quizzes}\\
%{200} & {tests}\\
%\underline{190} & {final}\\
%{500} & {total}
%\end{tabular}

%(Point totals will be normalized to these relative weights). 

\nd
{\bf Course Grades} Your grade will be based on a point total.   A: 90\% or above.    
B: 80-89\%.   C: 70-79\%.   D: 60-69\%.    F: 59\% or below. \\

\nd
{\bf Make-ups}  Makeups for exams will be given only in extreme circumstances in accordance with official University policy. Except for unforeseeable events, requests for a makeup must be made before the exam is given. There will be no make-ups for quizzes but you can drop two lowest quizzes. \\

%**If you know BEFORE an exam that you have a conflict, contact me in advance. In this case, it is sometimes possible to arrange an early exam.** 

\nd
{\bf Philosophy}   Real learning requires your active involvement. Practice on the 
{\bf homework} problems is strongly recommended. The result in a test usually reflects how much effort you have put into the {\bf homework} assignment as well as class learning, and how well you have prepared for it. The midterm exams will not be surprises, they will be related to the homework, quizzes and examples discussed in class. 

\bigskip
\noindent
{\bf Attendance policy:}  I expect you to attend all classes. %A grade penalty will be exact
By university policy, missing more than 10\%
of the scheduled class sessions, {\it whether excused or unexcused},
will result in a grade penalty.   If you plan to leave before class is over, the correct procedure
is to mention this to me before I start class.\\ %It is impolite, disruptive, and a bad idea to leave 
%class while I am lecturing unless you have followed this procedure. \\

\nd
{\bf Math Tutoring}     %Starting Jan. 17th.    
HOURS: 10:00 am - 4:00 pm, Monday-Thursday   (LC 105) 
and 6:00 pm - 8:00 pm, Monday-Thursday (Bates House, Columbia Hall, Sims). 
(Please also check the schedule posted outside LC 105 or visit 
{\em http://www.math.sc.edu/mathlab.html})
 %for possible change)

%Calculator.    The use of calculator is not allowed (and is not necessary) in exams, although it could be helpful for some homework and section quizzes. It is not required to have knowledge of operating your calculator (TI-82,83,...) at an advanced level. 

%\noindent
%{\bf Math Lab}{~(A free tutoring service, no appointment necessary):} 
%M--Th 10:00 am-4:00 pm (LeConte 105), opens Mon (8/28/06);
%M--Th 6:00-8:00 pm (Bates House, Columbia Hall, Sims), opens Tue (9/5/06).
%\\http://www.math.sc.edu/~$\tilde{}$ murphy
\end{document}
